---
title: "model anova"
author: "Ke"
date: '2018-09-13'
output:
  pdf_document: default
  html_document: default
---
```{r setup, include=FALSE}
library(lme4)
library(car)
load("/Users/kezhang/ownCloud/Suicide_UG/UG_clean_updated/ugDATA1.RData")
```

# Table 2
```{r}
Anova(m1g, type = 3)
```
**The omnibus term for the Group x Context interaction including all 4 groups and 3 contexts (baseline, empathy, punish) was $X^2$ = 26.29, p < .001.**


# Table 3
## Anger reactivity model
```{r}
Anova(manger, type = 3)
```
**The omnibus term for the Group x Context interaction including all 4 groups and 3 context (empathy, reputation, resources) was $X^2$ = 4.21, p = .648.**


## Sympathy reactivity model
```{r}
Anova(msympathy, type = 3)
```
**The omnibus term for the Group x Context interaction including all 4 groups and 3 context was $X^2$ = 5.53, p = .477.**


## Fairness reactivity model
```{r}
Anova(mFair, type = 3)
```
**The omnibus term for the Group x Context interaction including all 4 groups and 3 context was $X^2$ = 21.72, p = .001.**

# Supplementary Table 1
```{r}
Anova(m3gPun, type = 3)
summary(m3gPun)
stargazer(summary(m3gPun)$coefficient, type = "text")
write.csv(round(summary(m3gPun)$coefficients, 3), "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/NoIndividual/group4InteractionPun3.csv")

```
**The omnibus term for the Group x Context interaction including all 4 groups and 4 context (baseline, empathy, reputation, resources) was $X^2$ = 41.00, p < .001.**