---
title: "UG_data_analysis1"
author: "Ke"
date: '2018-01-15'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
library(lme4)
library(ggplot2)
library(GGally)
library(plyr)
library(Matrix)
library(readxl)
library(reshape2)
library(numDeriv)
library(MuMIn)
library(glmulti)
library(rJava)
library(mice)
library(stargazer)
```


```{r data, echo=FALSE}
# import data
#task <- read.csv("/home/kzhang5/scratch/ug_all_task_data.csv")
#demo <- read_excel("/home/kzhang5/scratch/ug_demog.xlsx")
#question <- read_excel("/home/kzhang5/scratch/ug_questionnaire.xlsx")
#
#task <- read.csv("C:\\Users\\ke\\ownCloud\\Suicide_UG\\UG_clean_updated\\ug_all_task_data.csv")
#demo <- read_excel("C:\\Users\\ke\\ownCloud\\Suicide_UG\\UG_clean_updated\\ug_demog.xlsx")
#question <- read_excel("C:\\Users\\ke\\ownCloud\\Suicide_UG\\UG_clean_updated\\ug_questionnaire.xlsx")


task <- read.csv("/Users/kezhang/ownCloud/Suicide_UG/UG_clean_updated/ug_all_task_data.csv")
demo <- read_excel("/Users/kezhang/ownCloud/Suicide_UG/UG_clean_updated/ug_demog.xlsx")
question <- read_excel("/Users/kezhang/ownCloud/Suicide_UG/UG_clean_updated/ug_questionnaire.xlsx")

question <- rename(question, c("UPPSP NEG URGENCY" = "urgency"))
demoQuestion <- merge(demo, question, on = "ID")
allData <- merge(task, demoQuestion, on = "ID")
allData$totalStake <- allData$PlayerProposedAmount + allData$OpponentProposedAmount
allData <- rename(allData, c("HOUSEHOLD INCOME" = "HouseholdIncome", "HRSD NO SUI" = "HRSD_NO_SUI", "PER CAPITA INCOME" = "IncomePerCapita", "MMSE TOTAL" = "MMSE"))
allData$Fairness_score <- as.factor(allData$Fairness_score)
allData$ID <- as.factor(allData$ID)
allData$AcceptOffer <- as.factor(allData$AcceptOffer)

# reference group = control
allData <- within(allData, group4 <- relevel(group4, ref = "control"))
allData <- within(allData, group5 <- relevel(group5, ref = "control"))

# block number
allData$block <- NA
allData$block <- ifelse(allData$merged_trial < 27, "1", ifelse((allData$merged_trial > 26) & (allData$merged_trial < 53), "2", "3" ))
```

variables in the models:
 - Reappraisal Direction
 - total stake
 - Fairness score
 - clinical groups
 - education
 - IncomePerCapita
 - EXIT (4 missing values)
 - trial number (within block number)
 - block number
 - an impulsivity measure: BIS_NONPLAN (3 missing values)/UPPS negative urgency
 - an interpersonal function measure: IIP15INTAMBV (4 missing values)

```{r missing values, include=FALSE}
# complete missing values
# check how many percentage of data is missing in the question dataframe
pMiss <- function(x){sum(is.na(x))/length(x)*100}
missingVar <- c('ID', 'BIS_NONPLAN', 'IIP15INTAMBV', 'EXIT', 'urgency')
missingDF <- question[, missingVar]
apply(question[missingVar], 2, pMiss)
print(md.pattern(question[missingVar]))

# impute data
missingDF_impute <- mice(missingDF, m = 5, meth = "pmm", maxit = 50)
missingVar_complete <- complete(missingDF_impute, 1)

# rename the columns with missing values in the original dataframe
allData <- rename(allData, c("BIS_NONPLAN" = "BIS_NONPLAN_miss", "IIP15INTAMBV" = "IIP15INTAMBV_miss", "EXIT" = "EXIT_miss", "urgency" = "urgency_miss"))

# merge the generated values to the df
allData <- merge(allData, missingVar_complete, by = "ID")
which(is.na(allData$EXIT))
```

# Whether HLM is needed?
## Intercept only
$$Accept\,Offer = 1$$
```{r}
interceptOnly <- glm(task$AcceptOffer ~ 1, family = binomial, data = task)
stargazer(interceptOnly, type = "text")
```

## Null model: random intercept only
$$Accept\,Offer = 1 + (1|ID)$$
```{r}
randomInterceptOnly <- glmer(task$AcceptOffer ~ 1 + (1|id), data = task, family = binomial)
stargazer(randomInterceptOnly, type = "text")
```
By adding the ID (nested), the AIC (1|D) is smaller than the AIC (1). So HLM is necessary. 

The variance of the intercept in the *null model is 1.157*. That is the variance can't be explained by the random effect of ID. Compare the variance with more complicated models. If the intercept variance gets smaller, that is an indication of the additional predictors adding more explanation to the DV.

##  Intraclass Correlation (ICC)
Test if HLM is needed: whether there is variation over the level 2 variable (participant ID). If the ICC > 0, then HLM is needed.
```{r, echo=FALSE}
ICC_model <- function(modelName) {
  tau_null <- as.numeric(lapply(summary(modelName)$varcor, diag))
  sigma_null <- as.numeric(attr(summary(modelName)$varcor, "sc")^2)
  ICC_null <- tau_null/(tau_null + sigma_null)
  return(ICC_null)
}

cat("ICC is", ICC_model(randomInterceptOnly))
```
The ICC > 0, the HLM is needed.

# correlation matrix of the subject level variables
```{r corr, echo=FALSE}
ggpairs(demoQuestion[, c("PER CAPITA INCOME", "HRSD NO SUI", "EDUCATION", "EXIT", "BIS_NONPLAN", "IIP15INTAMBV", "urgency")])
```
The following variables are moderately/highly correlated:
DRS x income, **education x income**, **EXIT x education**, **BIS nonplan x income**, BIS nonplan x HSD, **interpersonal x BIS nonplan**, urgency x HSD, urgency x BIS nonplan, **urgency x interpersonal**.

```{r wrapper, include=FALSE}
glmer.glmulti <- function(formula, data, random = ""){
  glmer(paste(deparse(formula), random), data = data, family = binomial, control = glmerControl(calc.derivs = FALSE))
}
```

# Level 1 model (Random intercept and fixed slopes with random effect (1|ID))
## No interaction model

$$Accept\,Offer = Reappraisal\,Direction + scale(total\,Stake) + Fairness\,score + (1|ID)$$
```{r}
m0 <- glmer(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score + (1|ID), family = binomial, data = allData, control = glmerControl(optimizer = "bobyqa"))
stargazer(m0, type = "text")
```

# Level 1 model with $group$ predictor (random effect (1|ID))
## No interaction effect
The model with 4 groups and 5 groups:
$$Accept\,Offer = Reappraisal\,Direction + totalStake + Fairness\,score + group4 + (1|ID)$$
```{r, echo=FALSE}
m3 <- glmer(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score + group4 + (1|ID), family = binomial, data = allData, control = glmerControl(optimizer = "bobyqa"))

m3_1 <- glmer(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score + group5 + (1|ID), family = binomial, data = allData, control = glmerControl(optimizer = "bobyqa"))

print("model with 4 groups")
stargazer(m3, type = "text")

print("model with 5 groups")
stargazer(m3_1, type = "text")

```
Clinically groups are not significantly different from HC in terms of gamble acceptance.

### The model with an individual subject level variable
$$Accept\,Offer = Reappraisal\,Direction + scale(total\,Stake) + Fairness\,score + group4 + VAR + (1|ID)$$
```{r, echo=FALSE}
m_education <- update(m3, .~. + scale(EDUCATION))
m_income <- update(m3, .~. + scale(IncomePerCapita))
m_exit <- update(m3, .~. + scale(EXIT))
m_mmse <- update(m3, .~. + scale(MMSE))
m_nonplan <- update(m3, .~. + scale(BIS_NONPLAN))
m_urgency <- update(m3, .~. + scale(urgency))
m_interpersonal <- update(m3, .~. + scale(IIP15INTAMBV))

print("Education")
stargazer(m_education, type = "text")
print("income")
stargazer(m_income, type = "text")
print("EXIT")
stargazer(m_exit, type = "text")
print("MMSE")
stargazer(m_mmse, type = "text")
print("UPPSP NEG URGENCY")
stargazer(m_urgency, type = "text")
print("IIP15INTAMBV, interpersonal")
stargazer(m_interpersonal, type = "text")
print("nonplan")
stargazer(m_nonplan, type = "text")
```
$EXIT$ is the only subject level variable has significant influence on the gamble acceptance.

## Interaction effect models
Fit specific interaction models. From higher order to lower.

$$Accept\,Offer = Reappraisal\,Direction + scale(total\,Stake) + Fairness\,score + group4 + INTERACTION + (1|ID)$$

1.  $Reappraisal\,Direction$ x $scale(total\,Stake)$ x $Fairness\,score$ x $group4$ four way interaction effect, and see if the model is significant. If not, drop this interaction.

```{r, include = FALSE}
m2_4interaction <- glmer(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score + group4 + ReappraisalDirection * scale(totalStake) * Fairness_score * group4 + (1|ID), data = allData, family = binomial, glmerControl(calc.derivs = FALSE, optCtrl = list(maxfun = 2e4)))

stargazer(m2_4interaction, type = "text")
```
It failed to converge at 4 way interaction

2. $ReappraisalDirection$ x $Fairness_score$ x $group4$ three way interaction
```{r, include = FALSE, echo=FALSE}
m2_3interaction1 <- glmer(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score + group4 + ReappraisalDirection * Fairness_score * group4 + (1|ID), data = allData, family = binomial, control = glmerControl(calc.derivs = FALSE, optCtrl = list(maxfun = 2e4)))

stargazer(m2_3interaction1, type = "text")
```
It failed to converge.

3. $Reappraisal\,Direction$ x $scale(total\,Stake)$ x $group4$ three way interaction
```{r, echo=FALSE}
m2_3interaction2 <- glmer(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score + group4 + ReappraisalDirection * scale(totalStake) * group4 + (1|ID), data = allData, family = binomial, control = glmerControl(optimizer = "bobyqa"))

stargazer(m2_3interaction2, type = "text")
```
$Reappraisal\,Direction$ x $scale(total\,Stake)$ x $group4$ has weak significant influence on gamble acceptance.

4. $fairness\, score$ x $group4$ two way interaction
```{r, echo=FALSE}
m2_2interaction1 <- glmer(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score * group4 + (1|ID), data = allData, family = binomial, control = glmerControl(optimizer = "bobyqa"))
stargazer(m2_2interaction1, type = "text")
```
Fairness score and group has significant interaction.

5. $reappraisal\, direction$ x $group4$ two way interaction
```{r, echo=FALSE}
m2_2interaction2 <- glmer(allData$AcceptOffer ~ scale(totalStake) + Fairness_score + ReappraisalDirection * group4 + (1|ID), data = allData, family = binomial, control = glmerControl(optimizer = "bobyqa"))
stargazer(m2_2interaction2, type = "text")
```
reappraisal direction x group4 has significant interaction.

6. $fairness\, score$ x $group4$ two way interaction
```{r, echo=FALSE}
m2_2interaction3 <- glmer(allData$AcceptOffer ~ scale(totalStake) + ReappraisalDirection + Fairness_score  * group4 + (1|ID), data = allData, family = binomial, control = glmerControl(optimizer = "bobyqa"))
stargazer(m2_2interaction3, type = "text")
```
fairness score x group4 has significant interaction.

7. $total\, stake$ x $group4$ two way interaction
```{r, echo=FALSE}
m2_2interaction4 <- glmer(allData$AcceptOffer ~ scale(totalStake) + ReappraisalDirection + Fairness_score + group4 + scale(totalStake) * group4 + (1|ID), data = allData, family = binomial, control = glmerControl(optimizer = "bobyqa"))
stargazer(m2_2interaction4, type = "text")
```
total stake x group4 has significant interaction.

8. $total\, stake$ x $fairness\, score$ two way interaction
```{r, echo=FALSE}
m2_2interaction5 <- glmer(allData$AcceptOffer ~ scale(totalStake) + ReappraisalDirection + Fairness_score + group4 + scale(totalStake) * Fairness_score + (1|ID), data = allData, family = binomial, control = glmerControl(optimizer = "bobyqa"))
stargazer(m2_2interaction5, type = "text")
```
total stake x fairness score has significant interaction.

**Select the best model among the interaction models:**
```{r, echo=FALSE}
modellist1 <- model.sel(m2_3interaction2, m2_2interaction1, m2_2interaction2, m2_2interaction3, m2_2interaction4, m2_2interaction5)
print(modellist1)

anova(m2_3interaction2, m2_2interaction2)
```
The 3 way interaction is no significantly better than the 2 way interaction. Hence, The best interaction model is $Reappraisal\,Direction$ x $scale(total\,Stake) x group4$:
```{r, echo=FALSE}
stargazer(m2_3interaction2, type = "text")
```

**the (best) interaction model with the subject level variable**
$$Accept\,Offer = Reappraisal\,Direction + scale(total\,Stake) + Fairness\,score + group4 + \\Reappraisal\,Direction * scale(total\,Stake) * group4 + VAR+ (1|ID)$$
```{r, echo=FALSE}
m_education1 <- update(m2_3interaction2, .~. + scale(EDUCATION))
m_income1 <- update(m2_3interaction2, .~. + scale(IncomePerCapita))
m_exit1 <- update(m2_3interaction2, .~. + scale(EXIT))
m_mmse1 <- update(m2_3interaction2, .~. + scale(MMSE))
m_nonplan1 <- update(m2_3interaction2, .~. + scale(BIS_NONPLAN))
m_urgency1 <- update(m2_3interaction2, .~. + scale(urgency))
m_interpersonal1 <- update(m2_3interaction2, .~. + scale(IIP15INTAMBV))

print("EXIT is the only significant var.")
stargazer(m_exit1, type = "text")
```

Only $EXIT$, among all the subject level variable has significant influence in the gamble acceptance.

**2 way interaction model $reappraisal\, direction$ x $group4$ with subject level vars:**
```{r, echo=FALSE}
m_education4 <- update(m2_2interaction2, .~. + scale(EDUCATION))
m_income4 <- update(m2_2interaction2, .~. + scale(IncomePerCapita))
m_exit4 <- update(m2_2interaction2, .~. + scale(EXIT))
m_mmse4 <- update(m2_2interaction2, .~. + scale(MMSE))
m_nonplan4 <- update(m2_2interaction2, .~. + scale(BIS_NONPLAN))
m_urgency4 <- update(m2_2interaction2, .~. + scale(urgency))
m_interpersonal4 <- update(m2_2interaction2, .~. + scale(IIP15INTAMBV))


print("EXIT is the only significant var.")
stargazer(m_exit4, type = "text")
```
The following variable has significant influence in this interaction model:
$EXIT$.

The following codes is for the random effect (block|ID), they are using the same procedure with above model with random effect (1|ID).

# Level 1 model (Random intercept and random slopes with random effect (block|ID))
## No interaction model

$$Accept\,Offer = Reappraisal\,Direction + scale(total\,Stake) + Fairness\,score + (block|ID)$$
```{r, echo=FALSE}
m5 <- glmer(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score + (block|ID), family = binomial, data = allData, control = glmerControl(optimizer = "bobyqa"))

stargazer(m5, type = "text")
```

# Level 1 model with $group$ predictor (random effect (block|ID))
## No interaction effect
With 4 clinical groups and 5 groups.
```{r, echo=FALSE}
m7 <- glmer(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score + group4 + (block|ID), family = binomial, data = allData, control = glmerControl(optimizer = "bobyqa"))

m7_1 <- glmer(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score + group5 + (block|ID), family = binomial, data = allData, control = glmerControl(optimizer = "bobyqa"))

print("model with 4 groups")
stargazer(m7, type = "text")
print("model with 5 groups")
stargazer(m7_1, type = "text")
```
Clinically groups is not significantly influence the gamble acceptance compared to HC in model with no interaction effect. And $group4$ and $group5$ have the same influence.

### the model with the an individual subject level variable
$$Accept\,Offer = Reappraisal\,Direction + scale(total\,Stake) + Fairness\,score + group4 + VAR + (block|ID)$$
```{r, echo=FALSE}
m_education2 <- update(m7, .~. + scale(EDUCATION))
m_income2 <- update(m7, .~. + scale(IncomePerCapita))
m_exit2 <- update(m7, .~. + scale(EXIT))
m_mmse2 <- update(m7, .~. + scale(MMSE))
m_nonplan2 <- update(m7, .~. + scale(BIS_NONPLAN))
m_urgency2 <- update(m7, .~. + scale(urgency))
m_interpersonal2 <- update(m7, .~. + scale(IIP15INTAMBV))

print("EXIT model")
stargazer(m_exit2, type = "text")

print("NONPLAN model")
stargazer(m_nonplan2, type = "text")
```
$EXIT$ is the only significant subject level variable.

In the model with $nonplan$ variable, the depression group is different to accept gamble compared to the HC. 

## models with interaction effect
Fit specific interaction models. From higher order to lower.

$$Accept\,Offer = Reappraisal\,Direction + scale(total\,Stake) + Fairness\,score + group4 + INTERACTION + (block|ID)$$

1.  $ReappraisalDirection$ x $scale(totalStake)$ x $Fairness\,score$ x $group4$ four way interaction effect, and see if the model is significant. If not, drop this interaction.

```{r, include=FALSE}
m9_4interaction <- glmer(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score + group4 + ReappraisalDirection * scale(totalStake) * Fairness_score * group4 + (block|ID), data = allData, family = binomial, glmerControl(calc.derivs = FALSE, optCtrl = list(maxfun = 2e4)))

stargazer(m9_4interaction)
```
It failed to converge at 4 way interaction

2. $ReappraisalDirection$ x $Fairness\,score$ x $group4$ three way interaction
```{r, include=FALSE}
m9_3interaction1 <- glmer(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score + group4 + ReappraisalDirection * Fairness_score * group4 + (block|ID), data = allData, family = binomial, glmerControl(calc.derivs = FALSE, optCtrl = list(maxfun = 2e4)))
```
It failed to converge.

3. $Reappraisal\,Direction$ x $scale(total\,Stake)$ x $group4$ three way interaction
```{r, echo=FALSE}
m9_3interaction <- glmer(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score + group4 + ReappraisalDirection * scale(totalStake) * group4 + (block|ID), data = allData, family = binomial, glmerControl(calc.derivs = FALSE, optCtrl = list(maxfun = 2e4)))
stargazer(m9_3interaction, type = "text")
```
Reappraisal Direction x totalStake x group4 is marginally significant.

4. $fairness\, score$ x $group4$ two way interaction
```{r, echo=FALSE}
m9_2interaction1 <- glmer(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score * group4 + (block|ID), data = allData, family = binomial, glmerControl(calc.derivs = FALSE, optCtrl = list(maxfun = 2e4)))

stargazer(m9_2interaction1, type = "text")
```
Fairness score x group has significant interaction effect.

5. $reappraisal\, direction$ x $group4$ two way interaction
```{r, echo=FALSE}
m9_2interaction2 <- glmer(allData$AcceptOffer ~ scale(totalStake) + Fairness_score + ReappraisalDirection * group4 + (block|ID), data = allData, family = binomial, control = glmerControl(optimizer = "bobyqa"))

stargazer(m9_2interaction2, type = "text")
```
reappraisal direction x group4 has significant influence.

6. $fairness\, score$ x $group4$ two way interaction
```{r, echo=FALSE}
m9_2interaction3 <- glmer(allData$AcceptOffer ~ scale(totalStake) + ReappraisalDirection + Fairness_score  * group4 + (block|ID), data = allData, family = binomial, control = glmerControl(optimizer = "bobyqa"))
stargazer(m9_2interaction3, type = "text")
```
fairness score x group4 has significant influence.

7. $total\, stake$ x $group4$ two way interaction
```{r}
m9_2interaction4 <- glmer(allData$AcceptOffer ~ scale(totalStake) + ReappraisalDirection + Fairness_score + group4 + scale(totalStake) * group4 + (block|ID), data = allData, family = binomial, control = glmerControl(optimizer = "bobyqa"))
stargazer(m9_2interaction4, type = "text")
```
total stake x group4 has significant influence.

8. $total\, stake$ x $fairness\, score$ two way interaction
```{r, echo=FALSE}
m9_2interaction5 <- glmer(allData$AcceptOffer ~ scale(totalStake) + ReappraisalDirection + Fairness_score + group4 + scale(totalStake) * Fairness_score + (block|ID), data = allData, family = binomial, control = glmerControl(optimizer = "bobyqa"))
stargazer(m9_2interaction5, type = "text")
```
total stake x fairness score has significant influence.

**which interaction model is the best model among all the interaction models:**
```{r, echo=FALSE}
modellist2 <- model.sel(m9_3interaction, m9_2interaction1, m9_2interaction2, m9_2interaction3, m9_2interaction4, m9_2interaction5)
print(modellist2)
```
The best interaction model is $Reappraisal\,Direction$ x $scale(total\,Stake)$ x $group4$ 3 way interaction.

**the (best) interaction model with the subject level variable**
$$Accept\,Offer = Reappraisal\,Direction + scale(total\,Stake) + Fairness\,score + group4 + \\Reappraisal\,Direction * scale(total\,Stake) * group4 + VAR + (block|ID)$$
```{r, echo=FALSE}
m_education3 <- update(m9_3interaction, .~. + scale(EDUCATION))
m_income3 <- update(m9_3interaction, .~. + scale(IncomePerCapita))
m_exit3 <- update(m9_3interaction, .~. + scale(EXIT))
m_mmse3 <- update(m9_3interaction, .~. + scale(MMSE))
m_nonplan3 <- update(m9_3interaction, .~. + scale(BIS_NONPLAN))
m_urgency3 <- update(m9_3interaction, .~. + scale(urgency))
m_interpersonal3 <- update(m9_3interaction, .~. + scale(IIP15INTAMBV))

stargazer(m_exit3, type = "text")
```

Only $EXIT$ has significant influence. 

Compare (1|ID) and (block|ID) $EXIT$ models:
```{r, echo=FALSE}
modellist3 <- model.sel(m_exit, m_exit1, m_exit2, m_exit3)
print(modellist3)
```