---
title: "UG suicide HLM"
author: "Ke"
date: '2018-01-10'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)

library(lme4)
library(ggplot2)
library(GGally)
library(plyr)
library(Matrix)
library(readxl)
library(reshape2)
library(numDeriv)
library(MuMIn)
library(glmulti)
library(rJava)
```

```{r, echo=FALSE, include=FALSE}
# Import and Clean data
task <- read.csv("/Users/kezhang/ownCloud/Suicide_UG/UG_clean_updated/ug_all_task_data.csv")
demo <- read_excel("/Users/kezhang/ownCloud/Suicide_UG/UG_clean_updated/ug_demog.xlsx")
question <- read_excel("/Users/kezhang/ownCloud/Suicide_UG/UG_clean_updated/ug_questionnaire.xlsx")

#task <- read.csv("C:\\Users\\ke\\ownCloud\\Suicide_UG\\UG_clean_updated\\ug_all_task_data.csv")
#demo <- read_excel("C:\\Users\\ke\\ownCloud\\Suicide_UG\\UG_clean_updated\\ug_demog.xlsx")
#question <- read_excel("C:\\Users\\ke\\ownCloud\\Suicide_UG\\UG_clean_updated\\ug_questionnaire.xlsx")

question <- rename(question, c("UPPSP NEG URGENCY" = "urgency"))
demoQuestion <- merge(demo, question, on = "ID")
allData <- merge(task, demoQuestion, on = "ID")
allData$totalStake <- allData$PlayerProposedAmount + allData$OpponentProposedAmount

allData <- rename(allData, c("HOUSEHOLD INCOME" = "HouseholdIncome", "HRSD NO SUI" = "HRSD_NO_SUI", "PER CAPITA INCOME" = "IncomePerCapita", "MMSE TOTAL" = "MMSE"))


allData$Fairness_score <- as.factor(allData$Fairness_score)
allData$ID <- as.factor(allData$ID)
allData$AcceptOffer <- as.factor(allData$AcceptOffer)

corrMatrix <- ggpairs(demoQuestion[, c("PER CAPITA INCOME", "HRSD NO SUI", "DRS", "EDUCATION", "EXIT", "BIS_NONPLAN", "IIP15INTAMBV", "urgency" )])
print(corrMatrix)
```

# Whether HLM is needed?
## Intercept only
```{r}
interceptOnly <- glm(task$AcceptOffer ~ 1, family = binomial, data = task)
print(summary(interceptOnly))
```

## Null model: random intercept only
```{r}
randomInterceptOnly <- glmer(task$AcceptOffer ~ 1 + (1|ID), data = task, family = binomial)
print(summary(randomInterceptOnly))
```
By adding the ID (nested), the AIC (1|D) is smaller than the AIC (1). So HLM is necessary. 

The variance of the intercept in the *null model is 1.157*. That is the variance can't be explained by the random effect of ID. Compare the variance with more complicated models. If the intercept variance gets smaller, that is an indication of the additional predictors adding more explanation to the DV.

##  Intraclass Correlation (ICC)
Test if HLM is needed: whether there is variation over the level 2 variable (participant ID). If the ICC > 0, then HLM is needed.
```{r}
ICC_model <- function(modelName) {
  tau_null <- as.numeric(lapply(summary(modelName)$varcor, diag))
  sigma_null <- as.numeric(attr(summary(modelName)$varcor, "sc")^2)
  ICC_null <- tau_null/(tau_null + sigma_null)
  return(ICC_null)
}

cat("ICC is", ICC_model(randomInterceptOnly))
```
The ICC > 0, the HLM is needed.

# Level 1 predictors (fairness score, stake size, context) and group 


## glmulti wrapper
```{r}
glmer.glmulti <- function(formula, data, random = ""){
  glmer(paste(deparse(formula), random), data = data, family = binomial, control = glmerControl(calc.derivs = FALSE))
}
```

The following models are exhaustve screening of alternative models, which including the interaction:
## Random intercept and fixed slopes
```{r}
m1 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score + group4, level = 2, fitfunction = glmer.glmulti, random = "+ (1|ID)", method = "g", data = allData)

m1_1 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection * scale(totalStake) * Fairness_score * group4, level = 2, fitfunction = glmer.glmulti, random = "+ (1|ID)", method = "g", data = allData)

summary(m1)
summary(m1_1)
```
## Random intercept and random slope (ReappraisalDirection|ID)
```{r}
# fail to converge
m2 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score + group4, level = 2, fitfunction = glmer.glmulti, random = "+ (ReappraisalDirection|ID)", method = "g", data = allData)

# fail to converge
m2_1 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection * scale(totalStake) * Fairness_score * group4, level = 2, fitfunction = glmer.glmulti, random = "+ (ReappraisalDirection|ID)", method = "g", data = allData)
summary(m2)
summary(m2_1)
```

## Random intercept and random slope (totalStake|ID)
```{r}
m3 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection * scale(totalStake) * Fairness_score * group4, level = 2, fitfunction = glmer.glmulti, random = "+ (totalStake|ID)", method = "g", data = allData)

summary(m3)
```


## Random intercept and random slope (totalStake|ID) + (ReappraisalDirection|ID)
```{r}
m5 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection * scale(totalStake) * Fairness_score * group4, level = 2, fitfunction = glmer.glmulti, random = "+ (totalStake|ID) + (ReappraisalDirection|ID)", method = "g", data = allData)

summary(m5)
```

## Random intercept and random slope (Fairness_score|ID) + (ReappraisalDirection|ID)
```{r}
# failed
m6 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection * scale(totalStake) * Fairness_score * group4, level = 2, fitfunction = glmer.glmulti, random = "+ (Fairness_score|ID) + (ReappraisalDirection|ID)", method = "d", data = allData)

summary(m6)
```


## Random intercept and random slope (Fairness_score|ID)
```{r}
# fail
m4 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection * scale(totalStake) * Fairness_score * group4, level = 2, fitfunction = glmer.glmulti, random = "+ (Fairness_score|ID)", method = "d", data = allData)

print(m4)
```

## Random intercept and random slope (Fairness_score|ID) + (totalStake|ID) + (ReappraisalDirection|ID)
```{r}
# fail to converge
m7 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection * scale(totalStake) * Fairness_score * group4, level = 2, fitfunction = glmer.glmulti, random = "+ (Fairness_score|ID) + (totalStake|ID) + (ReappraisalDirection|ID)", method = "d", data = allData)

summary(m7)
```

The following models are higher order interactions:
## ReappraisalDirection x scale(totalStake) x Fairness_score x group4
```{r}
m8 <- glmer(allData$AcceptOffer ~ ReappraisalDirection * scale(totalStake) * Fairness_score * group4 + (Fairness_score|ID) + (totalStake|ID) + (ReappraisalDirection|ID), data = allData, family = "binomial")

summary(m8)
```

## ReappraisalDirection x scale(totalStake) x Fairness_score
```{r}
m9 <- glmer(allData$AcceptOffer ~ ReappraisalDirection * scale(totalStake) * Fairness_score + group4 + (Fairness_score|ID) + (totalStake|ID) + (ReappraisalDirection|ID), data = allData, family = "binomial")

summary(m9)
```
## group4 x scale(totalStake) x Fairness_score 
```{r}
m10 <- glmer(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) * Fairness_score * group4 + (Fairness_score|ID) + (totalStake|ID) + (ReappraisalDirection|ID), data = allData, family = "binomial")

summary(m10)
```

## ReappraisalDirection x Fairness_score x group4
```{r}
m11 <- glmer(allData$AcceptOffer ~ scale(totalStake) + ReappraisalDirection * Fairness_score * group4 + (Fairness_score|ID) + (totalStake|ID) + (ReappraisalDirection|ID), data = allData, family = "binomial")

summary(m11)
```

## ReappraisalDirection x total stake x group4
```{r}
m12 <- glmer(allData$AcceptOffer ~ scale(totalStake) * ReappraisalDirection * group4 + Fairness_score + (Fairness_score|ID) + (totalStake|ID) + (ReappraisalDirection|ID), data = allData, family = "binomial")

summary(m12)
knit(UG_data_analysis_hypothesis.Rmd)
```

# Level 2 predictors 
The models include the demographics variables are imbalanced between the clinical groups: *education*, *household income*, *MMSE*, *SSI BL CURRENT* (only for psychiatric groups).
```{r}
m13 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection * scale(totalStake) * Fairness_score * group4 * scale(EDUCATION) * scale(HouseholdIncome) * scale(MMSE), exclude = c("MMSE:HouseholdIncome"), level = 2, fitfunction = glmer.glmulti, random = "+ (1|ID)", method = "d", data = allData)

```

## remove education
```{r}
m_edu <- glmulti(allData$AcceptOffer ~ ReappraisalDirection * scale(totalStake) * Fairness_score * group4 * scale(HouseholdIncome) * scale(MMSE), exclude = c("MMSE:HouseholdIncome"), level = 2, fitfunction = glmer.glmulti, random = "+ (1|ID)", method = "d", data = allData)
```

## remove income
```{r}
m_income <- glmulti(allData$AcceptOffer ~ ReappraisalDirection * scale(totalStake) * Fairness_score * group4 * scale(EDUCATION) *  scale(MMSE), level = 2, fitfunction = glmer.glmulti, random = "+ (1|ID)", method = "d", data = allData)

```

## remove MMSE
```{r}
m_mmse <- glmulti(allData$AcceptOffer ~ ReappraisalDirection * scale(totalStake) * Fairness_score * group4 * scale(EDUCATION) * scale(HouseholdIncome), level = 2, fitfunction = glmer.glmulti, random = "+ (1|ID)", method = "d", data = allData)

```

# pairwise interaction effects
```{r}
# wrapper exclude interaction MMSE x income
glmer.glmulti <- function(formula, data, random = ""){
  glmer(paste(deparse(formula), random), data = data, family = binomial, control = glmerControl(calc.derivs = FALSE), exclude = c("MMSE:HouseholdIncome"))
}

m_pairInter1 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score + group4 + scale(EDUCATION) + scale(HouseholdIncome) + scale(MMSE), level = 2, fitfunction = glmer.glmulti, random = "+ (1|ID)", method = "g", data = allData)

m_pairInter2 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score + group4 + scale(EDUCATION) + scale(HouseholdIncome) + scale(MMSE), level = 2, fitfunction = glmer.glmulti, random = "+ (Fairness_score|ID)", method = "g", data = allData)

m_pairInter3 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score + group4 + scale(EDUCATION) + scale(HouseholdIncome) + scale(MMSE), level = 2, fitfunction = glmer.glmulti, random = "+ (totalStake|ID)", method = "g", data = allData)

m_pairInter4 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score + group4 + scale(EDUCATION) + scale(HouseholdIncome) + scale(MMSE), level = 2, fitfunction = glmer.glmulti, random = "+ (ReappraisalDirection|ID)", method = "g", data = allData)

m_pairInter5 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score + group4 + scale(EDUCATION) + scale(HouseholdIncome) + scale(MMSE), level = 2, fitfunction = glmer.glmulti, random = "+ (ReappraisalDirection|ID) + (totalStake|ID)", method = "g", data = allData)

m_pairInter6 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score + group4 + scale(EDUCATION) + scale(HouseholdIncome) + scale(MMSE), level = 2, fitfunction = glmer.glmulti, random = "+ (Fairness_score|ID) + (totalStake|ID)", method = "g", data = allData)

m_pairInter7 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score + group4 + scale(EDUCATION) + scale(HouseholdIncome) + scale(MMSE), level = 2, fitfunction = glmer.glmulti, random = "+ (Fairness_score|ID) + (ReappraisalDirection|ID)", method = "g", data = allData)

m_pairInter8 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score + group4 + scale(EDUCATION) + scale(HouseholdIncome) + scale(MMSE), level = 2, fitfunction = glmer.glmulti, random = "+ (Fairness_score|ID) + (totalStake|ID) + (ReappraisalDirection|ID)", method = "g", data = allData)

print(m_pairInter1)
print(m_pairInter2)
print(m_pairInter3)
print(m_pairInter4)
print(m_pairInter5)
print(m_pairInter6)
print(m_pairInter7)
print(m_pairInter8)
```

# Longitudianl models
Because trial number influence participants choice in the baseline data. Here we run longitudinal models with time variables $Trial_Number$.
```{r baseline data}
allData$framingContext <- NA
allData$framingContext[allData$ReappraisalDirection == "punish"] <- "framing"
allData$framingContext[allData$ReappraisalDirection == "empathy"] <- "framing"
allData$framingContext[allData$ReappraisalDirection == "baseline"] <- "baseline"
baselineData <- subset(allData, allData$framingContext == "baseline")
```

## with various random effects
```{r}

m_l1 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection * scale(totalStake) * Fairness_score * group4 * scale(EDUCATION) * scale(HouseholdIncome) * scale(MMSE) + scale(merged_trial), exclude = c("MMSE:HouseholdIncome"), level = 2, fitfunction = glmer.glmulti, random = "+ (1|ID)", method = "g", data = allData)

m_l2 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection * scale(totalStake) * Fairness_score * group4 * scale(EDUCATION) * scale(HouseholdIncome) * scale(MMSE) + scale(merged_trial), exclude = c("MMSE:HouseholdIncome"), level = 2, fitfunction = glmer.glmulti, random = "+ (merged_trial|ID)", method = "g", data = allData)

m_l3 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection * scale(totalStake) * Fairness_score * group4 * scale(EDUCATION) * scale(HouseholdIncome) * scale(MMSE) + scale(merged_trial), exclude = c("MMSE:HouseholdIncome"), level = 2, fitfunction = glmer.glmulti, random = "+ (1|ID) + (0 + merged_trial|ID)", method = "g", data = allData)

m_l1_1 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection * scale(totalStake) * Fairness_score * group4 * scale(EDUCATION) * scale(HouseholdIncome) * scale(MMSE), level = 2, fitfunction = glmer.glmulti, random = "+ (1|ID)", method = "g", data = allData)

m_l2_1 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection * scale(totalStake) * Fairness_score * group4 * scale(EDUCATION) * scale(HouseholdIncome) * scale(MMSE), level = 2, fitfunction = glmer.glmulti, random = "+ (merged_trial|ID)", method = "g", data = allData)

m_l3_1 <- glmulti(allData$AcceptOffer ~ ReappraisalDirection * scale(totalStake) * Fairness_score * group4 * scale(EDUCATION) * scale(HouseholdIncome) * scale(MMSE), level = 2, fitfunction = glmer.glmulti, random = "+ (1|ID) + (0 + merged_trial|ID)", method = "g", data = allData)

anova(m_l1, m_l1_1)
anova(m_l2, m_l2_1)
anova(m_l3, m_l3_1)

print(m_l1)
print(m_l2)
print(m_l3)
print(m_l1_1)
print(m_l2_1)
print(m_l3_1)
```