---
title: "UG_data_analysis"
author: "Ke and Alex"
date: '2018-01-15'
outputs: text_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lme4)
library(ggplot2)
library(GGally)
library(plyr)
library(Matrix)
library(readxl)
library(reshape2)
library(numDeriv)
library(MuMIn)
# library(glmulti)
# library(rJava)
library(mice)
library(stargazer)
library(lsmeans)
library(effects)
library(psych)
library(compareGroups)
library(afex)
library(stargazer)
library(magrittr)
library(dplyr)
library(tidyverse)

```


```{r data, include = FALSE}
# import data

task <- read.csv("~/ownCloud/Suicide_UG/UG_clean_updated/ug_all_task_data149.csv")
demo <- read.csv("~/ownCloud/Suicide_UG/UG_clean_updated/ug_demog149.csv")
question <- read.csv("~/ownCloud/Suicide_UG/UG_clean_updated/ug_questionnaire.csv")
emoRating <- read.csv("~/ownCloud/Suicide_UG/UG_clean_updated/ug_reactivity149.csv")

# check number of participants 
print(length(unique(task$ID)))
print(length(demo$ID))
print(length(question$ID))
print(length(unique(emoRating$ID)))
question <- question[!duplicated(question),]
print(length(question$ID))
question$BIS_TOTAL <- question$BIS_TOTMEAN * 30

# merge demographics and questionniares. 
demoQuestion <- merge(demo, question[, c("ID", "HOUSEHOLD.INCOME", 
                                         "PER.CAPITA.INCOME", "HRSD.NO.SUI",
                                         "DEP.ONSET.AGE", "SIS.ML.TOTAL",
                                         "SIS.ML.PLAN", "SSI.BL.CURRENT", "MMSE.TOTAL",
                                         "EXIT", "DRS", "BIS_NONPLAN", "BIS_MOTOR",
                                         "BIS_COGNIT", "BIS_TOTMEAN", "BIS_TOTAL", "IIP15INTSEN",
                                         "IIP15INTAMBV", "IIP15AGRESS", "UPPSP.NEG.URGENCY",
                                         "UPPSP.POS.URGENCY", "UPPSP.LACK.OF.PREMED",
                                         "UPPSP.LACK.OF.PERSEV", "IRI_PERSPECTIVE_TAKING",
                                         "IRI_FANTASY_SCALE", "IRI_EMPATHETIC_CONCERN",
                                         "IRI_PERSONAL_DISTRESS", "GOALS", "IMPULSE",
                                         "AWARENESS", "WTARRAW", "WTARSS", "MAX.LETHALITY",
                                         "SIS.ML.PLAN", "SIS.ML.TOTAL")], on = "ID")
demoQuestion$IRI_cogEmpathy <- demoQuestion$IRI_FANTASY_SCALE + demoQuestion$IRI_PERSPECTIVE_TAKING
demoQuestion$IRI_affEmpathy <- demoQuestion$IRI_EMPATHETIC_CONCERN + demoQuestion$IRI_PERSONAL_DISTRESS

demoQuestion <- plyr::rename(demoQuestion, c("UPPSP.NEG.URGENCY" = "Nurgency", "UPPSP.POS.URGENCY" = "Purgency", "MMSE.TOTAL" = "MMSE"))

# compare the group differences
myVar <- c("EDUCATION", "GENDERTEXT", "PER.CAPITA.INCOME", "PROTECT2AGE", 
           "RACETEXT", "MMSE","WTARSS", "DRS", "EXIT", 
           "BIS_NONPLAN", "BIS_TOTAL", "Nurgency", "Purgency", "IIP15INTAMBV", "IIP15INTSEN", 
           "IIP15AGRESS", "MAX.LETHALITY", "SIS.ML.PLAN", "SIS.ML.TOTAL", 
           "IRI_cogEmpathy", "IRI_affEmpathy")

# "SSI.BL.CURRENT" "SSI.BL.CURRENT" = "Suicide Ideation Scale", 

idx <- match(myVar, names(demoQuestion))
# idx <- sort(c(idx-1, idx))
# c1 <- demoQuestion[, idx]
c1 <- demoQuestion[, myVar]
c1 <- plyr::rename(c1, c("PROTECT2AGE" = "Age", "EDUCATION" = "Education", "RACETEXT" = "Race", "HRSD.NO.SUI" = "Hamilton Rating Scale for Depression(no 16Q)", "GENDERTEXT" = "Gender", "WTARSS" = "Wechsler Test of Adult Reading Standardized Score", "DRS" = "Dementia Rating Scale", "EXIT" = "EXIT - Neuropsych Exam", "Nurgency" = "UPPSP Impulsive Behavior Scale - negative urgency", "Purgency" = "UPPSP Impulsive Behavior Scale - positive urgency", "PER.CAPITA.INCOME" = "Income Per Capita", "BIS_TOTAL" = "BIS Total", "MAX.LETHALITY" = "Beck Lethality scale", "SIS.ML.PLAN" = "Suicide Intent Scale (Planning subscale)", "SIS.ML.TOTAL" = "Suicide Intent Scale (Total)"))

c2 <- compareGroups(c1,demoQuestion$group4)
c2_2 <- compareGroups(c1, demoQuestion$group5, show.p.trend = T)
t1 <- createTable(c2, hide.no = 0, digits = 1, show.n = TRUE, show.p.mul = T)
t2_1 <- createTable(c2_2,hide = NA, hide.no = 0, digits = 1, show.n = TRUE, show.p.mul = T)

export2csv(tssi, file = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/group4IRI.csv")


noControldemo <- subset(demoQuestion, demoQuestion$group4 != "control") 
noControlDepdemo <- subset(demoQuestion, !demoQuestion$group4 %in% c("control", "depression")) 
noControldemo$group4 <- factor(noControldemo$group4)
noControldemo$group5 <- factor(noControldemo$group5)
noControlDepdemo$group4 <- factor(noControlDepdemo$group4)
noControlDepdemo$group5 <- factor(noControlDepdemo$group5)

ssi <- compareGroups(as.data.frame(noControlDepdemo[, c("SSI.BL.CURRENT")]), noControlDepdemo$group4)
ssi1 <- compareGroups(as.data.frame(noControlDepdemo[, c("SSI.BL.CURRENT")]), noControlDepdemo$group5)
tssi1 <- createTable(ssi1, hide = NA, hide.no = 0, digits = 1, show.n = TRUE, show.p.mul = T)
tssi <- createTable(ssi, hide = NA, hide.no = 0, digits = 1, show.n = TRUE, show.p.mul = T)
HRSD <- compareGroups(as.data.frame(noControldemo[, c("HRSD.NO.SUI")]), noControldemo$group4)
tHRSD <- createTable(HRSD, hide = NA, hide.no = 0, digits = 1, show.n = TRUE, show.p.mul = T)
sis <- compareGroups(as.data.frame(noControldemo[, c("SIS.ML.TOTAL")]), noControldemo$group4)
tsis <- createTable(sis, hide = NA, hide.no = 0, digits = 1, show.n = TRUE, show.p.mul = T)

attempter <- subset(demoQuestion, demoQuestion$group4 == "attempter")
attempter$group5 <- factor(attempter$group5)
catt1 <- compareGroups(attempter[, c("MAX.LETHALITY", "SIS.ML.PLAN", "SIS.ML.TOTAL")], attempter$group5)
catt <- compareGroups(attempter[, c("MAX.LETHALITY", "SIS.ML.PLAN", "SIS.ML.TOTAL")], attempter$group4)

tcatt1 <- createTable(catt1, hide = NA, hide.no = 0, digits = 1, show.n = TRUE, show.p.mul = T)
tcatt <- createTable(catt, hide = NA, hide.no = 0, digits = 1, show.n = TRUE, show.p.mul = T)

export2csv(t2_1, file = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/demo5.csv")

task$check <- 1:dim(task)[1]
task_no_duplicates <- task %>% group_by(ID, merged_trial, Stimuli_RT) %>% filter(row_number(check) == 1)
t <- table(task$ID, task$ReappraisalDirection)
plot(t)

t_nodupes <- table(task_no_duplicates$ID, task_no_duplicates$ReappraisalDirection)
plot(t_nodupes)


# ID 221242 has missing trials in empathy and baseline
ID221242 <- subset(task, task$ID == 221242)
print(nrow(ID221242))
print(nrow(subset(ID221242, ID221242$ReappraisalDirection == "empathy")))
print(nrow(subset(ID221242, ID221242$ReappraisalDirection == "punish")))
print(nrow(subset(ID221242, ID221242$ReappraisalDirection == "baseline")))

allData <- merge(task_no_duplicates, demoQuestion, on = "ID")

allData$totalStake <- allData$PlayerProposedAmount + allData$OpponentProposedAmount
allData <- plyr::rename(allData, c("HOUSEHOLD.INCOME" = "HouseholdIncome", "HRSD.NO.SUI" = "HRSD_NO_SUI", "PER.CAPITA.INCOME" = "IncomePerCapita", "MMSETOTAL" = "MMSE"))

allData$Fairness_score <- as.numeric(allData$Fairness_score)
allData$ID <- as.factor(allData$ID)
allData$AcceptOffer <- as.factor(allData$AcceptOffer)
allData$Trial_Number <- as.factor(allData$Trial_Number)

# reference group = attempter
allData <- within(allData, group4 <- relevel(group4, ref = "attempter"))
allData <- within(allData, group5 <- relevel(group5, ref = "AttempterHL"))
emoRating <- within(emoRating, group4 <- relevel(group4, ref = "attempter"))
emoRating <- within(emoRating, group5 <- relevel(group5, ref = "AttempterHL"))

# block number
allData$block <- NA
allData$block <- ifelse(allData$merged_trial < 27, "1", ifelse((allData$merged_trial > 26) & (allData$merged_trial < 53), "2", "3" ))
allData$block <- as.factor(allData$block)

# fairness ratio
allData$fairLR <- log(allData$PlayerProposedAmount/allData$OpponentProposedAmount)
allData$fairR <- (allData$PlayerProposedAmount/allData$OpponentProposedAmount)

levels(allData$group4)[levels(allData$group4) == "control"] <- "Control"
levels(allData$group4)[levels(allData$group4) == "attempter"] <- "Attempter"
levels(allData$group4)[levels(allData$group4) == "ideator"] <- "Ideator"
levels(allData$group4)[levels(allData$group4) == "depression"] <- "Depression"


allData[, c("PlayerProposedAmount", "OpponentProposedAmount")]
# separate groups
depression <- subset(allData, group4 == "depression")
control <- subset(allData, group4 == "control")
ideator <- subset(allData, group4 == "ideator")
attempter <- subset(allData, group4 == "attempter")
attHL <- subset(allData, group5 == "AttempterHL")
attLL <- subset(allData, group5 == "AttempterLL")

#Pvars <- allData[, c("ID", "MMSE", "PROTECT2AGE", "GENDERTEXT", "IncomePerCapita", "HRSD_NO_SUI", "EDUCATION", "RACETEXT", "WTARSS", "DRS", "EXIT", "BIS_NONPLAN", "urgency", "IIP15INTAMBV", "IIP15INTSEN", "IIP15AGRESS", "IRI_EMPATHETIC_CONCERN")]
#Pvars <- subset(Pvars, !duplicated(ID))
#emoRating <- merge(emoRating, Pvars, by = "ID")
emoRating$ReappraisalDirection[emoRating$ReappraisalDirection == 1] <- "punish"
emoRating$ReappraisalDirection[emoRating$ReappraisalDirection == 2] <- "empathy"
emoRating$ReappraisalDirection <- as.factor(emoRating$ReappraisalDirection)

# save.image("/Volumes/LAB/Suicide_UG/UG_data_analysis/ugDATA.RData")
load("/Users/kezhang/Dropbox/ugDATA1.RData")
```

```{r fisher}
fisherDf <- table(demoQuestion$PER.CAPITA.INCOME, demoQuestion$group4)
fisher.test(fisherDf)  
chisq.test(fisherDf, simulate.p.value = TRUE) 
fisher.test()
aov(demoQuestion$PROTECT2AGE~demoQuestion$group4)
c <- subset(demoQuestion, demoQuestion$group4 == "control")

race <- demoQuestion %>%
  select(RACETEXT, group4) %>%
  mutate(RACETEXTcode = ifelse(RACETEXT == "WHITE", "WHITE", "NON-WHITE"))
tb <- table(race$group4, race$RACETEXTcode)
chisq.test(tb)
fisher.test(tb)

tb <- table(demoQuestion$EDUCATION, demoQuestion$group4)
chi <- fisher.test(tb)
a <- aov(demoQuestion$EDUCATION~demoQuestion$group4)
TukeyHSD(a)

```


variables in the models:
 - Reappraisal Direction
 - total stake
 - Fairness score
 - clinical groups
 - education
 - IncomePerCapita
 - EXIT (4 missing values)
 - trial number (within block number)
 - block number
 - an impulsivity measure: BIS_NONPLAN (3 missing values)/UPPS negative urgency
 - an interpersonal function measure: IIP15INTAMBV (4 missing values)
 
```{r gamble acceptance}
fairAcceptPercDftmp <- 
  allData[, c("ID", "AcceptOffer", "Fairness_score", "fairness", "group4")] %>%
  group_by(ID) %>%
  summarise(fairAcceptPerc = round(100*sum(AcceptOffer == 1 & fairness == "fair")/
              sum(fairness == "fair"), 2), 
            unfairRejectPerc = round(100*sum(AcceptOffer == 0 & fairness == "unfair")/
                                       sum(fairness == "unfair"), 2))

fairAcceptPercDf <- merge(demoQuestion[, c("ID", "group4", "group5")], 
                        fairAcceptPercDftmp, on = "ID")


fairAcceptPercDftmp <- 
  allData[, c("ID", "AcceptOffer", "Fairness_score", "fairness", "group4")] %>%
  # group_by(ID) %>%
  summarise(sumRej = sum(AcceptOffer == 0), sumAcce = sum(AcceptOffer == 0),
            sumUnfair = sum(fairness == "unfair"), sumFair = sum(fairness == "fair"),
            sumRejUnfair = sum(AcceptOffer == 0 & fairness == "unfair"),
            sumAccefair = sum(AcceptOffer == 1 & fairness == "fair"))

unique(fairAcceptPercDftmp$sumUnfair)
unique(fairAcceptPercDftmp$sumFair)

nrow(subset(allData, allData$AcceptOffer == 0 & allData$fairness == "unfair"))
nrow(subset(allData, allData$AcceptOffer == 1 & allData$fairness == "fair"))
nrow(subset(allData, allData$fairness == "unfair"))/3
nrow(subset(allData, allData$fairness == "fair"))/2

nrow(rejUnfair)/nrow(subset(allData, allData$fairness == "unfair"))


print("participants accept % fair offer")
mean(fairAcceptPercDf$fairAcceptPerc)

print("accept reject % most unfair offer")
mean(fairAcceptPercDf$unfairRejectPerc)
```

```{r rm missing values, include = False}
# the columns with missing values
criticalMissingVar <- c('ID', 'BIS_NONPLAN', 'IIP15INTAMBV', "IIP15INTSEN", "IIP15AGRESS", 'EXIT', 'Purgency', "Nurgency", "DRS")
names(which(colSums(is.na(allData))>0))
```

```{r impute missing values, include=FALSE}
# check how many percentage of data is missing in the question dataframe
# pMiss <- function(x){sum(is.na(x))/length(x)*100}
# missingVar <- c('ID', 'BIS_NONPLAN', 'IIP15INTAMBV', 'EXIT', 'urgency')
# missingDF <- question[, missingVar]
# apply(question[missingVar], 2, pMiss)
# print(md.pattern(question[missingVar]))

# impute data
# missingDF_impute <- mice(missingDF, m = 5, meth = "pmm", maxit = 50)
# print(summary(missingDF_impute))
# missingVar_complete <- complete(missingDF_impute,1)

# merge the generated values to the df
# missingVar_complete <- rename(missingVar_complete, c("BIS_NONPLAN" = "BIS_NONPLAN_full", "IIP15INTAMBV" = "IIP15INTAMBV_full", "EXIT" = "EXIT_full", "urgency" = "urgency_full"))
# allData <- merge(allData, missingVar_complete, by = "ID")
# df <- allData
```


# correlation matrix of the subject level variables
```{r corr, echo=FALSE}
ggpairs(allData[, c("IncomePerCapita", "HRSD_NO_SUI", "DRS", "EDUCATION", "EXIT", 
            "BIS_NONPLAN", "IIP15INTAMBV", "Purgency", "Nurgency")])
```
The following variables are moderately/highly correlated:
- DRS x income
- **education x income**
- education x DRS
- EXIT x DRS
- **EXIT x education**
- **BIS nonplan x income**
- BIS nonplan x HSD
- **interpersonal x BIS nonplan**
- urgency x HSD
- urgency x BIS nonplan
- **urgency x interpersonal**

# models$1|ID|block$
# Level 1 models (no group interaction)
$$offer = reappraisal direction & stake & fairness$$
```{r}
# fairness scores
m0 <- glmer(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + Fairness_score + (1|ID/block), family = binomial, data = allData,  
  control = glmerControl(optimizer = "bobyqa"))
summary(m0)

# fair Log Ratio
m0r <- glmer(allData$AcceptOffer ~ ReappraisalDirection + scale(totalStake) + fairLR + (1|ID/block), family = binomial, data = allData, 
  control = glmerControl(optimizer = "bobyqa"))
summary(m0r)
car::Anova(m0r)
anova(m0,m0r)
lsm <- lsmeans(m0r, "ReappraisalDirection")
plot(lsm, horiz = F)
plot(Effect("totalStake",m0r), axes = list(y=list(lab = "P(accept)", type = "response", lim = c(0,1))), multiline = TRUE, rug = FALSE)
plot(Effect("fairLR",m0r), axes = list(y=list(lab = "P(accept)", type = "response", lim = c(0,1))), multiline = TRUE, rug = FALSE)

# 3 way interaction
m1 <- glmer(allData$AcceptOffer ~ ReappraisalDirection*fairLR*scale(totalStake) + (1|ID/block), family = binomial, data =
              allData, control = glmerControl(optimizer = "bobyqa"))
summary(m1)
car::Anova(m1)
anova(m0r,m1)
lsm <- lsmeans(m1, "ReappraisalDirection", by = "totalStake", at = list(totalStake = c(8, 13,18)))
plot(lsm, horiz = F)
lsm <- lsmeans(m1, "fairLR", by = "totalStake", at = list(totalStake = c(8, 13,18), fairLR = c(-2.66,-1.22,0.22)))
plot(lsm, horiz = F)
lsm <- lsmeans(m1, "ReappraisalDirection", by = "totalStake", at = list(totalStake = c(8, 13,18)))
plot(lsm, horiz = F)
```
The $ReappraisalDirection*fairLR*scale(totalStake)$ is the best fit model.

# level 1 and 2 interact with groups
$$offer = reappraisal\,direction & stake & fairness & groups$$
```{r main model}
# 4 way interaction: ReappraisalDirection * scale(fairLR) * scale(totalStake) * group. Too complex to converge. 
#m1_4way <- glmer(allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) * group4 +  (1 | ID/block), family = binomial, data = allData, control = glmerControl(optimizer = "bobyqa"), optCtrl = list(maxfun = 2e4))


# Group three way interaction
m1g <-glmer(
  AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection * group4 + scale(fairLR) * group4 + scale(totalStake) * group4 +  (1 | ID/block),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa"))

stargazer(m1g, title = "AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection * group4 + scale(fairLR) * group4 + scale(totalStake) * group4 +  (1 | ID/block)", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/NoIndividual/group4Interaction.txt")

stargazer(m1g,
          dep.var.labels = "Accept Offer", type = "html",
          covariate.labels = c("Empathy", "Punish", "Fairness", "Stake size",
                               "Control", "Depression", "Ideator", "Empathy $ \times$ Fairness",
                               "Punish $ \times$ Fairness", "Empathy x Stake size", 
                               "Punish x Stake size", "Fairness x Stake size", 
                               "Empathy x Control", "Punish x Control", 
                               "Empathy x Depression", "Punish x Depression",
                               "Empathy x Ideator", "Punish x Ideator", 
                               "Fairness x Control", "Fairness x Depression",
                               "Fairness x Ideator", "Stake size x Control",
                               "Stake size x Depression", "Stake size x Ideator",
                               "Empathy x Fairness x Stake size", 
                               "Punish x Fairness x Stake size"),
          out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/NoIndividual/group4Interaction.tex")

tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/NoIndividual/UGcontext*fair*stake.tiff', 
     units="in", height = 4, width = 5, res=300)
lsm <- lsmeans(m1g, "ReappraisalDirection", by = c("totalStake", "fairLR"), 
               at = list(totalStake = c(8, 13,18), fairLR = c(-2.66,-1.22,0.22)))
plot(lsm, horiz = F, fill = ReappraisalDirection) + 
  theme(axis.text.x=element_text(angle=90, hjust=1)) +
  ggtitle("UGcontext*fair*total stake")
  
dev.off()

tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/NoIndividual/UGcontext*group4.tiff', 
     units="in", height = 5, width = 12, res=300)
lsm <- lsmeans(m1g, "ReappraisalDirection", by = "group4")
lsmDf <- lsm[1:12]
lsmDf <- as.data.frame(lsmDf)

ggplot(lsmDf, aes(ReappraisalDirection, lsmean)) +
  geom_errorbar(aes(ymin = lsmean - SE, ymax = lsmean + SE), width = .1,
                position=position_dodge(.1)) +
  geom_point() +
  xlab("Reappraisal Context") +
  ylab("Least Squares Mean") +
  theme_bw(base_size = 14) +
  facet_grid(~ group4) +
  scale_x_discrete(labels = c("Baseline", "Empathy", "Punish"), expand=c(0.05,0.40)) +
  theme(axis.title.x = element_text(margin = margin(t = 15)),
        axis.title.y = element_text(margin = margin(r = 15)),
        panel.spacing = unit(2, "lines"),
        strip.text.x = element_text(size = 16))
        
dev.off()

tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/NoIndividual/UGfair*group4.tiff', 
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(m1g, "fairLR", by = "group4", at = list(fairLR = c(-2.66,-1.22,0.22)))
plot(lsm, horiz = F)
dev.off() 

tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/NoIndividual/UGstake*group4.tiff', 
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(m1g, "totalStake", by = "group4", at = list(totalStake = c(8, 13,18)))
plot(lsm, horiz = F)
dev.off()

tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/NoIndividual/UGstake*UGfair.tiff', 
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(m1g, "totalStake", by = "fairLR", at = list(totalStake = c(8, 13,18),
                                                           fairLR = c(-2.66,-1.22,0.22)))
plot(lsm, horiz = F)
dev.off()

tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/NoIndividual/UGcontext*UGfair.tiff', 
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(m1g, "ReappraisalDirection", by = c("fairLR"), 
               at = list(fairLR = c(-2.66,-1.22,0.22)))
plot(lsm, horiz = F) +
  ggtitle("UGcontext*fair")
  
dev.off()


tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/NoIndividual/UGcontext*UGstake.tiff', 
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(m1g, "ReappraisalDirection", by = c("totalStake"), 
               at = list(totalStake = c(8, 13,18)))
plot(lsm, horiz = F) +
  ggtitle("UGcontext*fair")
  
dev.off()

tb <- stargazer(summary(m1g)$coefficients,
          covariate.labels = c("Independent variables", "Estimate", 
                               "Standard error", "z", "p"), type = "text",
          digits = 2)
          # out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/NoIndividual/group4Interaction1.tex")

write.csv(round(summary(m1g)$coefficients, 2), "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/NoIndividual/group4Interaction.csv")
```

```{r}
# NB: there are RT outliers up to 430s (??).  Try without the top 5%:
m1g_cens <- glmer(
  AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 +  (1 |
  ID/block),
  family = binomial,
  data = allData[allData$Stimuli_RT<5823,],
  
  control = glmerControl(optimizer = "bobyqa"))
  summary(m1g_cens)
car::Anova(m1g_cens)
# results are not sensitive to that
## tried context*fair*Group -- too complex, would not bother including

plot(m1g)
```

```{r covariate}
newdata <- allData[, c("AcceptOffer", "ReappraisalDirection", "fairLR", "totalStake",
                       "group4", "EXIT", "EDUCATION", "IIP15INTSEN",
                       "Gender", "IncomePerCapita", "BIS_NONPLAN", "IIP15INTAMBV",
                       "ID", "block", "DRS", "HRSD_NO_SUI")]
      
newdata$ID <- as.factor(newdata$ID)
newdata$block <- as.factor(newdata$block)
newdata$Gender <- as.factor(newdata$Gender)
newdata$group4 <- as.factor(newdata$group4)
newdata$AcceptOffer <- as.factor(newdata$AcceptOffer)
newdata$ReappraisalDirection <- as.factor(newdata$ReappraisalDirection)

# newdata[, c("ID", "block", "Gender", "group4", "AcceptOffer", "ReappraisalDirection")] <-
  # as.factor(newdata[, c("ID", "block", "Gender", "group4", "AcceptOffer", "ReappraisalDirection")])

newdata[, c("fairLR", "totalStake","EXIT", "EDUCATION", "IIP15INTSEN","IncomePerCapita", "BIS_NONPLAN", "IIP15INTAMBV", "DRS", "HRSD_NO_SUI")] <- scale(newdata[, c("fairLR", "totalStake","EXIT", "EDUCATION", "IIP15INTSEN","IncomePerCapita", "BIS_NONPLAN", "IIP15INTAMBV", "DRS", "HRSD_NO_SUI")])

newdataNA_omit <- newdata[complete.cases(newdata), ]
newdataOmit <- na.omit(newdata)

tiff("/Users/kezhang/Desktop/ctgr.tiff", units="in", height = 15, width = 15, res=300)
ggpairs(na.omit(allData[,c("fairLR", "totalStake",
                       "EXIT", "EDUCATION", "IIP15INTSEN", "IncomePerCapita", 
                       "BIS_NONPLAN", "IIP15INTAMBV", "HRSD_NO_SUI", "DRS",
                       "IIP15AGRESS", "MMSE")]))
dev.off()
tiff("/Users/kezhang/Desktop/ctgr.tiff", units="in", height = 15, width = 15, res=300)
ct <- ggpairs(newdataNA.omit[, c("AcceptOffer", "ReappraisalDirection", "fairLR", "totalStake",
                       "EXIT", "EDUCATION", "IIP15INTSEN", "IncomePerCapita", 
                       "BIS_NONPLAN", "IIP15INTAMBV")])
dev.off()
#      
# options(na.action = "na.omit")
# options(na.action = "na.fail")

mc2 <-
  glmer(
  AcceptOffer ~ ReappraisalDirection * fairLR *  
    totalStake + ReappraisalDirection * group4 + fairLR *  
    group4 + totalStake * group4 + ReappraisalDirection *  
    EXIT + EDUCATION * group4 * ReappraisalDirection +  
    IIP15INTSEN * group4 * ReappraisalDirection + Gender *  
    ReappraisalDirection + IncomePerCapita * group4 +  
    BIS_NONPLAN * group4 * ReappraisalDirection + 
    IIP15INTAMBV * group4 * ReappraisalDirection +
    (1 | ID/block),
  family = binomial,
  data = na.omit(newdata),
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

mc3 <-
  glmer(
    AcceptOffer ~ ReappraisalDirection * fairLR *  
    totalStake + ReappraisalDirection * group4 + fairLR *  
    group4 + totalStake * group4 + 
      ReappraisalDirection *  EXIT +
      EDUCATION * group4 * ReappraisalDirection +  
      IIP15INTSEN * group4 * ReappraisalDirection + 
      Gender * ReappraisalDirection +  
      DRS * group4 + 
      HRSD_NO_SUI * group4 +
      (1 | ID/block),
    family = binomial,
  data = na.omit(newdata),
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

mc4 <- update(mc3, .~. + ReappraisalDirection * DRS * group4)
mc5 <- update(mc3, .~. + HRSD_NO_SUI *ReappraisalDirection)
mc6 <- update(mc3, .~. + HRSD_NO_SUI *ReappraisalDirection*group4)
mc7 <- update(mc6, .~. + ReappraisalDirection * DRS * group4)

modelTable <- model.sel(mc3, mc4, mc5, mc6, mc7)
stargazer(summary(mc7)$coefficients, type = "text", title = "AcceptOffer ~ ReappraisalDirection * fairLR *  totalStake + ReappraisalDirection * group4 + fairLR *  group4 + totalStake * group4 + ReappraisalDirection *  EXIT + EDUCATION * group4 * ReappraisalDirection +  IIP15INTSEN * group4 * ReappraisalDirection + Gender * ReappraisalDirection +  ReappraisalDirection * DRS * group4 + HRSD_NO_SUI *ReappraisalDirection*group4 + (1 | ID/block)", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/individualCharacterModel1.txt")


tiff("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGcontext*group4.tiff",
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(mc7, "ReappraisalDirection", by = "group4")
plot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(~ group4)
dev.off()

tiff("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGfair*group4.tiff",
      units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(mc7, "fairLR", by = "group4", at = list(fairLR = c(-2.66,-1.22,0.22)))
plot(lsm, horiz = F) +
  facet_grid(~group4)
dev.off() 


tiff("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGcontext*totalStake.tiff",
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(mc7, "totalStake", by = "ReappraisalDirection", at = list(totalStake = c(8, 13,18)))
plot(lsm, horiz = F) +
  facet_grid(~ ReappraisalDirection)
dev.off()

lsm <- lsmeans(m1gPun, "AcceptOffer_lag")
plot(lsm, horiz = F)
dev.off()


lsm <- lsmeans(mc7, "ReappraisalDirection", by = c("EXIT", "group4"), at = list(EXIT = c(5, 10, 15)))
tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGcontext*EXIT.tiff', 
     units="in", height = 8, width = 10, res=300)
plot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(.~ EXIT + group4)  + ggtitle("UGcontext*EXIT")
dev.off()


lsm <- lsmeans(mc7, "ReappraisalDirection", by = c("EXIT", "group4"), at = list(EXIT = c(5, 10, 15)))
tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGcontext*EXIT*group4.tiff', 
     units="in", height = 8, width = 10, res=300)
plot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(.~ EXIT + group4)  + ggtitle("UGcontext*EXIT*group4")
dev.off()

lsm <- lsmeans(mc7, "ReappraisalDirection", by = c("DRS", "group4"), at = list(DRS = c(130, 135, 140)))
tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGcontext*DRS*group4.tiff', 
     units="in", height = 8, width = 10, res=300)
plot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(.~ DRS + group4)  + ggtitle("UGcontext*DRS*group4")
dev.off()

lsm <- lsmeans(mc7, "ReappraisalDirection", by = c("HRSD_NO_SUI", "group4"), at = list(HRSD_NO_SUI = c(5, 15, 25)))
tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGcontext*HRSD_NO_SUI*group4.tiff', 
     units="in", height = 8, width = 10, res=300)
plot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(.~ HRSD_NO_SUI + group4)  + ggtitle("UGcontext*HRSD_NO_SUI*group4")
dev.off()

lsm <- lsmeans(mc7, "HRSD_NO_SUI", by = "group4", at = list(HRSD_NO_SUI = c(5, 15, 25)))
tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/HRSD_NO_SUI*group4.tiff', 
     units="in", height = 8, width = 10, res=300)
plot(lsm, horiz = F)  +
    facet_grid(.~ group4)  + ggtitle("HRSD_NO_SUI*group4")
dev.off()

tiff("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGcontext*gender.tiff",
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(mc7, "Gender", by = "ReappraisalDirection")
plot(lsm, horiz = F) +
  facet_grid(~ ReappraisalDirection)
dev.off()

tiff("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGcontext*group4.tiff",
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(mc7, "ReappraisalDirection", by = "group4")
plot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(~ group4)
dev.off()


lsm <- lsmeans(mc7, "ReappraisalDirection", by = c("IIP15INTSEN", "group4"), at = list(IIP15INTSEN = c(3,5,10)))
tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGcontext*IIP15INTSEN*group4.tiff', 
     units="in", height = 8, width = 10, res=300)
plot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(.~ IIP15INTSEN + group4)  + ggtitle("UGcontext*IIP15INTSEN*group4")
dev.off()


lsm <- lsmeans(mc7, "ReappraisalDirection", by = c("EDUCATION", "group4"), at = list(EDUCATION = c(13,15,16)))
tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGcontext*EDUCATION*group4.tiff', 
     units="in", height = 8, width = 10, res=300)
plot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(.~ EDUCATION + group4)  + ggtitle("UGcontext*EDUCATION*group4")
dev.off()


```

```{r control MMSE EXIT}
# no missing values
# control for MMSE with (1 | ID)
m1gm <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection
  *group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + ReappraisalDirection*scale(MMSE) + (1|ID),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa"))
car::Anova(m1gm, type = 'III')
pdf("UGcontext*MMSE.pdf", width=8, height=6)
lsm <- lsmeans(m1gm, "ReappraisalDirection", by = "MMSE", at = list(MMSE = c(26,28,30)))
plot(lsm, horiz = F)
dev.off()

m1gE <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection
  *group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + ReappraisalDirection*scale(EXIT) + (1|ID),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa"))

m1gENI <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection
  *group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + ReappraisalDirection + scale(EXIT) + (1|ID),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa"))

#____________________________________________________________________________________________________________________

# control for MMSE with (1 | ID/block)
## ReappraisalDirection*scale(MMSE)
### This model is the best
m1gm_1 <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + ReappraisalDirection*scale(MMSE) + (1 | ID/block),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
stargazer(summary(m1gm_1)$coefficients, type = "text", title = "AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection * group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + ReappraisalDirection*scale(MMSE) + (1 | ID/block)", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGcontext*MMSE.txt")
car::Anova(m1gm_1, type = 'III')
tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGcontext*MMSE.tiff', 
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(m1gm_1, "ReappraisalDirection", by = c("MMSE", "group4"), at = list(MMSE = c(26,28,30)))
print(lsm)
plot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(.~ MMSE + group4)  + ggtitle("UGcontext*MMSE")
dev.off()

m1gE_1 <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + ReappraisalDirection*scale(EXIT) + (1 | ID/block),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
stargazer(m1gE_1, type = "text", title = "AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection * group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + ReappraisalDirection*scale(EXIT) + (1 | ID/block)", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGcontext*EXIT12.txt")
car::Anova(m1gm_1, type = 'III')
lsm <- lsmeans(m1gE_1, "ReappraisalDirection", by = c("EXIT", "group4"), at = list(EXIT = c(5, 10, 15)))
tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGcontext*EXIT.tiff', 
     units="in", height = 8, width = 10, res=300)
plot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(.~ EXIT + group4)  + ggtitle("UGcontext*EXIT")
dev.off()
#___________________________________Above best model ____________________________________________________

## ReappraisalDirection*scale(MMSE)*group4
m1gm_2 <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + ReappraisalDirection*scale(MMSE)*group4 + (1 | ID/block),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
lsm <- lsmeans(m1gm_2, "ReappraisalDirection", by = c("MMSE", "group4"), at = list(MMSE = c(26,28,30)))
ggplot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(.~ MMSE + group4)

m1gE_2 <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + ReappraisalDirection*scale(EXIT)*group4 + (1 | ID/block),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))

m1gE_3 <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + scale(EXIT)*group4 + (1 | ID/block),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))

anova(m1gm_2, m1gm_1)
summary(m1gm_2)
```

```{r demo}
mDemo1 <-
  glmer(
  AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + 
    ReappraisalDirection * group4 + 
    scale(fairLR) * group4 + 
    scale(totalStake) * group4 +
    scale(EDUCATION) * group4 * ReappraisalDirection + 
    scale(IncomePerCapita) * group4 * ReappraisalDirection +
    scale(HRSD_NO_SUI) * group4 * ReappraisalDirection +
    scale(DRS) * group4 * ReappraisalDirection +
    (1 | ID/block),
  family = binomial,
  data = allData,
  nAGQ = 0,  
  control = glmerControl(optimizer = "bobyqa"))

stargazer(round(summary(mDemo1)$coefficients, 2), out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/demoContrl.txt",
          title = "Controlling demographics")
write.csv(round(summary(mDemo1)$coefficients, 2),
          "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/demoContrl.csv")

lsm <- lsmeans(mDemo1, "ReappraisalDirection", by = "group4")
tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/demoContrl.tiff', 
     units="in", height = 8, width = 10, res=300)
plot(lsm, horiz = F) +
  facet_grid(.~ group4) +
  ggtitle("Controlling Education, Income, HRSD, DRS")
dev.off()
```

```{r control IRI}
# IRI affective empathy
## Interpersonal Reactivity Index - Empathetic Concern subscale
mIRI1 <-
  glmer(
  AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + 
    ReappraisalDirection * group4 + 
    scale(fairLR) * group4 + 
    scale(totalStake) * group4 +
    group4*scale(IRI_affEmpathy) + (1 | ID/block),
  family = binomial,
  data = allData,
  nAGQ = 0,  
  control = glmerControl(optimizer = "bobyqa"))
summary(m1gi)
car::Anova(m1gi, type = 'III')
pdf("UGcontext*IRIemp.pdf", width=12, height=6)
lsm <- lsmeans(m1gi, "ReappraisalDirection", by = "IRI_EMPATHETIC_CONCERN", at = list(IRI_EMPATHETIC_CONCERN = c(8,20,25)))
plot(lsm, horiz = F)
dev.off()

pdf("UGcontext*group_adjusted_IRIemp.pdf", width=8, height=6)
lsm <- lsmeans(m1gi, "ReappraisalDirection", by = "group4")
plot(lsm, horiz = F)
dev.off()

# better
mIRI2 <-
  glmer(
  AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + 
    ReappraisalDirection * group4 + 
    scale(fairLR) * group4 + 
    scale(totalStake) * group4 +
    group4*scale(IRI_affEmpathy)*ReappraisalDirection + (1 | ID/block),
  family = binomial,
  data = allData,
  nAGQ = 0,  
  control = glmerControl(optimizer = "bobyqa"))

stargazer(mIRI2, type = "text", title = "AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection * group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + ReappraisalDirection*scale(IRI_affEmpathy)*group4 + (1 | ID/block)", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/individual covariate models/UGcontext*IRI*group4.txt")

write.csv(round(summary(mIRI2)$coefficients, 2), 
          "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/individual covariate models/UGcontext*IRI*group4.csv")

tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/individual covariate models/IRI*group4.tiff', 
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(mIRI2, "IRI_affEmpathy", by ="group4", at = list(IRI_affEmpathy = c(23, 30, 40)))
plot(lsm, horiz = F) +
  facet_grid(.~ group4) +
  xlab("IRI Affective Empathy")
dev.off()

tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/individual covariate models/contrlIRI_UGcontext*group4.tiff', 
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(mIRI2, "ReappraisalDirection", by ="group4")
plot(lsm, horiz = F) +
  facet_grid(.~ group4)
dev.off()
```

```{r control interpersonal}
# Interpersonal aggression and sensitivity
m1ga <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + 
      ReappraisalDirection*scale(IIP15AGRESS) + (1 | ID/block),
  na.action=na.exclude,
  family = binomial,
  data = allData,
  nAGQ = 0,  
  control = glmerControl(optimizer = "bobyqa"))
  summary(m1ga)
car::Anova(m1ga, type = 'III')
pdf("UGcontext*IIPaggr.pdf", width=12, height=6)
lsm <- lsmeans(m1ga, "ReappraisalDirection", by = "IIP15AGRESS", at = list(IIP15AGRESS = c(0,4,11)))
plot(lsm, horiz = F)
dev.off()


m1gex <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + 
      ReappraisalDirection*scale(IIP15INTSEN) + (1 | ID/block),
  na.action=na.exclude,
  family = binomial,
  data = allData,
  nAGQ = 0,  
  control = glmerControl(optimizer = "bobyqa"))
  summary(m1gex)
car::Anova(m1gex, type = 'III')


lsm <- lsmeans(m1gex, "ReappraisalDirection", by = "IIP15INTSEN", at = list(IIP15INTSEN = c(3,5,10)))
plot(lsm, horiz = F)
dev.off()

# 3way interaction better
m1ga_1 <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + 
      ReappraisalDirection*scale(IIP15AGRESS)*group4 + (1 | ID/block),
  na.action=na.exclude,
  family = binomial,
  data = allData,
  nAGQ = 0,  
  control = glmerControl(optimizer = "bobyqa"))

stargazer(m1ga_1, type = "text", title = "AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + 
      ReappraisalDirection*scale(IIP15AGRESS)*group4 + (1 | ID/block)", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGcontext*IIP15AGRESS*group4.txt")
jpeg("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGcontext*IIP15AGRESS*group4.jpg")
lsm <- lsmeans(m1ga_1, "ReappraisalDirection", by = c("IIP15AGRESS", "group4"), at = list(IIP15AGRESS = c(3, 10, 16)))
plot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(.~ IIP15AGRESS + group4) 


m1gex_1 <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + 
      ReappraisalDirection*scale(IIP15INTSEN)*group4 + (1 | ID/block),
  na.action=na.exclude,
  family = binomial,
  data = allData,
  nAGQ = 0,  
  control = glmerControl(optimizer = "bobyqa"))

stargazer(m1gex_1, type = "text", title = "AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + 
      ReappraisalDirection*scale(IIP15INTSEN)*group4 + (1 | ID/block)", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGcontext*IIP15INTSEN*group4.txt")
jpeg("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGcontext*IIP15INTSEN*group4.jpg")
lsm <- lsmeans(m1gex_1, "ReappraisalDirection", by = c("IIP15INTSEN", "group4"), at = list(IIP15INTSEN = c(4, 9, 15)))
plot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(.~ IIP15INTSEN + group4) 

anova(m1ga_1, m1ga)
anova(m1gex_1, m1gex)


```

```{r income}
mIncome <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + 
    ReappraisalDirection * group4 + 
    scale(fairLR) * group4 + 
    scale(totalStake) * group4 + 
    ReappraisalDirection*scale(IncomePerCapita)*group4 + (1 | ID/block),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))

stargazer(summary(mIncome)$coefficients, type = "text", digits = 3, title = "AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + ReappraisalDirection*scale(IncomePerCapita)*group4 + (1 | ID/block)", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/individual covariate models/SES.txt")
write.csv(round(summary(mIncome)$coefficients, 3), "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/individual covariate models/SES.csv")

tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/individual covariate models/SESControl_group4*UGcontext.tiff', 
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(mIncome, "ReappraisalDirection", by = "group4")
plot(lsm, horiz = F) +
  facet_grid(.~group4) +
  ggtitle("Controlling SES")
dev.off()
tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/individual covariate models/SES*group4.tiff', 
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(mIncome, "IncomePerCapita", by = "group4", 
               at = list(IncomePerCapita = c(10625,20500,31250)))
plot(lsm, horiz = F) +
  facet_grid(.~ group4) +
  ggtitle("SES across groups") +
  scale_x_discrete(labels = c("low(25%)", "mdn(50%)", "high(75%)"))
dev.off()

tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/individual covariate models/SES*UGcontext.tiff', 
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(mIncome, "IncomePerCapita", by = "ReappraisalDirection", 
               at = list(IncomePerCapita = c(10625,20500,31250)))
plot(lsm, horiz = F) +
  facet_grid(.~ ReappraisalDirection) +
  ggtitle("SES across Reappraisal Direction") +
  scale_x_discrete(labels = c("low(25%)", "mdn(50%)", "high(75%)"))
dev.off()

stargazer(mIncome, type = "text")
```

```{r drs}
mDRS <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + 
    ReappraisalDirection * group4 + 
    scale(fairLR) * group4 + 
    scale(totalStake) * group4 + 
    ReappraisalDirection*scale(DRS)*group4 + (1 | ID/block),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))

stargazer(summary(mDRS)$coefficients, type = "text", digits = 3, title = "AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *group4 + scale(fairLR) * group4 + mDRS(totalStake) * group4 + ReappraisalDirection*scale(DRS)*group4 + (1 | ID/block)", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/individual covariate models/DRS.txt")

write.csv(round(summary(mDRS)$coefficients,3), "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/individual covariate models/DRS.csv")

tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/individual covariate models/DRSControl_group4*UGcontext.tiff', 
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(mDRS, "ReappraisalDirection", by = "group4")
plot(lsm, horiz = F) +
  facet_grid(.~ group4) +
  ggtitle("Controlling DRS")
dev.off()

tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/individual covariate models/DRS*group4.tiff', 
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(mDRS, "DRS", by = "group4", at = list(DRS = c(134.0, 138.0, 140.0)))
plot(lsm, horiz = F) +
  facet_grid(.~ group4) +
  ggtitle("DRS across groups") +
  scale_x_discrete(labels = c("low(25%)", "mdn(50%)", "high(75%)"))
dev.off()

tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/individual covariate models/DRS*UGcontext.tiff', 
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(mDRS, "DRS", by = "ReappraisalDirection", 
               at = list(DRS = c(134.0, 138.0, 140.0)))
plot(lsm, horiz = F) +
  facet_grid(.~ ReappraisalDirection) +
  ggtitle("DRS across Reappraisal Direction") +
  scale_x_discrete(labels = c("low(25%)", "mdn(50%)", "high(75%)"))
dev.off()
```

```{r education}

m1gEd_1 <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + ReappraisalDirection*scale(EDUCATION) + (1 | ID/block),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))



m1gEd_2 <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + group4*scale(EDUCATION) + (1 | ID/block),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa",optCtrl = list(maxfun = 2e4)))


## ReappraisalDirection*scale(Ed)*group4

### best model 
m1gEd_3 <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + ReappraisalDirection*scale(EDUCATION)*group4 + (1 | ID/block),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
lsm <- lsmeans(m1gm_2, "ReappraisalDirection", by = c("MMSE", "group4"), at = list(MMSE = c(26,28,30)))
ggplot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(.~ MMSE + group4)

stargazer(m1gEd_3, type = "text", title = "AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + ReappraisalDirection*scale(EDUCATION)*group4 + (1 | ID/block)", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGcontext*Edu*group4.text")
lsm <- lsmeans(m1gEd_3, "ReappraisalDirection", by = c("EDUCATION", "group4"), at = list(EDUCATION = c(12, 16, 20)))
tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGcontext*Edu*group4.tiff', 
     units="in", height = 8, width = 10, res=300)
plot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(.~ EDUCATION + group4)  + ggtitle("UGcontext*Edu*group4")
dev.off()
```

```{r SSI.BL.CURRENT}
noControlDep <- allData %>% filter(!group4 %in% c("Control", "Depression"))
noControlDep$group4 <- factor(noControlDep$group4)

mSSI <-
  glmer(
  AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + 
    ReappraisalDirection * group4 + 
    scale(fairLR) * group4 + 
    scale(totalStake) * group4 + 
    group4*scale(`SSI.BL.CURRENT`)*ReappraisalDirection + 
    (1 | ID/block),
  family = binomial,
  data = noControlDep,
  control = glmerControl(optimizer = "bobyqa",optCtrl = list(maxfun = 2e4)))

write.csv(round(summary(mSSI)$coefficients, 3), "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/individual covariate models/SSIBLCURRENT.csv")

tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/individual covariate models/SSIControl_group4*UGcontext.tiff', 
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(mSSI, "ReappraisalDirection", by = "group4")
plot(lsm, horiz = F) +
  facet_grid(.~ group4) +
  ggtitle("Controlling SSI BL CURRENT")
dev.off()

tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/individual covariate models/SSI*group4.tiff', 
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(mSSI, "SSI.BL.CURRENT", by = "group4", at = list(SSI.BL.CURRENT = c(14,19,25)))
plot(lsm, horiz = F) +
  facet_grid(.~ group4) +
  ggtitle("SSI.BL.CURRENT across groups") +
  scale_x_discrete(labels = c("low(25%)", "mdn(50%)", "high(75%)"))
dev.off()

tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/individual covariate models/SSI*UGcontext.tiff', 
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(mSSI, "SSI.BL.CURRENT", by = "ReappraisalDirection", 
               at = list(SSI.BL.CURRENT = c(14,19,25)))
plot(lsm, horiz = F) +
  facet_grid(.~ ReappraisalDirection) +
  ggtitle("SSI.BL.CURRENT across Reappraisal Direction") +
  scale_x_discrete(labels = c("low(25%)", "mdn(50%)", "high(75%)"))
dev.off()
```

```{r BIS_NONPLAN BIS_total}

mBIS_total <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + 
    ReappraisalDirection * group4 + 
    scale(fairLR) * group4 + 
    scale(totalStake) * group4 + 
    ReappraisalDirection*scale(BIS_TOTAL)*group4 + (1 | ID/block),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))

write.csv(round(summary(mBIS_total)$coefficients,3), '/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/individual covariate models/BIStotal.csv')

tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/individual covariate models/BIStotalControl_group4*UGcontext.tiff', 
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(mBIS_total, "ReappraisalDirection", by = "group4")
plot(lsm, horiz = F) +
  facet_grid(.~ group4) +
  ggtitle("Controlling BIS TOTAL")
dev.off()

tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/individual covariate models/BIStotal*group4.tiff', 
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(mBIS_total, "BIS_TOTAL", by = "group4", at = list(BIS_TOTAL = c(34.25, 41.50, 53.50)))
plot(lsm, horiz = F) +
  facet_grid(.~ group4) +
  ggtitle("BIS TOTAL across groups") +
  scale_x_discrete(labels = c("low(25%)", "mdn(50%)", "high(75%)"))
dev.off()

tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/individual covariate models/BIStotal*UGcontext.tiff', 
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(mBIS_total, "BIS_TOTAL", by = "ReappraisalDirection", 
               at = list(BIS_TOTAL = c(134.0, 138.0, 140.0)))
plot(lsm, horiz = F) +
  facet_grid(.~ ReappraisalDirection) +
  ggtitle("BIS TOTAL across Reappraisal Direction") +
  scale_x_discrete(labels = c("low(25%)", "mdn(50%)", "high(75%)"))
dev.off()

```

```{r IIP15INTSEN}
m1gIIPSEN_1 <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + scale(IIP15INTSEN)*group4 + (1 | ID/block),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
stargazer(m1gIIPSEN_1, type = "text", title = "AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + scale(IIP15INTSEN)*group4 + (1 | ID/block) + ReappraisalDirection*scale(BIS_NONPLAN)*group4 + (1 | ID/block)", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/IIP15INTSEN*group4.text")


m1gIIPSEN_3 <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + ReappraisalDirection*scale(IIP15INTSEN) + (1 | ID/block),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))

m1gIIPSEN_2 <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + ReappraisalDirection*scale(IIP15INTSEN) + (1 | ID/block),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
stargazer(m1gIIPSEN_2, type = "text", title = "AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection * group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + ReappraisalDirection*scale(IIP15INTSEN) + (1 | ID/block)", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGcontext*IIP15INTSEN*group4.text")

```

```{r IIP15AGRESS}
m1gIIPAGR_1 <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + scale(IIP15AGRESS)*group4 + (1 | ID/block),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
stargazer(m1gIIPAGR_1, type = "text", title = "AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + scale(IIP15INTSEN)*group4 + (1 | ID/block) + ReappraisalDirection*scale(BIS_NONPLAN)*group4 + (1 | ID/block)", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/IIP15INTSEN*group4.text")

m1gIIPAGR_2 <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + scale(IIP15AGRESS)*group4*ReappraisalDirection + (1 | ID/block),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))


```

```{r gender}
m1gGen_3 <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + ReappraisalDirection*Gender + Gender * group4+ (1 | ID/block),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))

stargazer(m1gGen_2, type = "text", title = "AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection * group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + ReappraisalDirection*Gender + (1 | ID/block)", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/ReappraisalDirection*Gender.text")

```

```{r Nurgency}
m1gPurgent_1 <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + scale(Purgency)*group4 + (1 | ID/block),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
# stargazer(m1gNurgent_1, type = "text", title = "AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + scale(IIP15INTSEN)*group4 + (1 | ID/block) + ReappraisalDirection*scale(BIS_NONPLAN)*group4 + (1 | ID/block)", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/IIP15INTSEN*group4.text")


m1gPurgent_2 <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + ReappraisalDirection*scale(Purgency) + (1 | ID/block),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
stargazer(m1gPurgent_2, type = "text", title = "AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection * group4 + scale(fairLR) * group4 + scale(totalStake) * group4 + ReappraisalDirection*scale(Purgency) + (1 | ID/block)", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGcontext*Purgency.text")
```

```{r control lethality}
# with lethality by group5
m1gl <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group5 + scale(fairLR) * group5 + scale(totalStake) * group5  + (1 | ID/block),
  family = binomial,
  data = allData,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
stargazer(m1gl, type = "text", title = "AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection * group5 + scale(fairLR) * group5 + scale(totalStake) * group5  + (1 | ID/block)", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/NoIndividual/group5Interaction.txt")

car::Anova(m1gl)
anova(m1g,m1gl)

jpeg("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/NoIndividual/UGcontext*group5.jpg")
lsm <- lsmeans(m1gl, "ReappraisalDirection", by = "group5")
plot(lsm, horiz = F) +
  theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(~ group5)
dev.off()
jpeg("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/NoIndividual/UGfair*group5.jpg")
lsm <- lsmeans(m1gl, "fairLR", by = "group5", at = list(fairLR = c(-2.66,-1.22,0.22)))
plot(lsm, horiz = F) +
  theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(~ group5)
dev.off()
jpeg("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/NoIndividual/UGstake*group5.jpg")
lsm <- lsmeans(m1gl, "totalStake", by = "group5", at = list(totalStake = c(8, 13,18)))
plot(lsm, horiz = F)+
  theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(~ group5)
dev.off()

plot(Effect("ReappraisalDirection*group4", mc7))
plot(Effect("totalStake",m0r), axes = list(y=list(lab = "P(accept)", type = "response", lim = c(0,1))), multiline = TRUE, rug = FALSE)

summary("ReappraisalDirection:group4:EDUCATION", mc7)
```




```{r replica}
# try to replicate previous UG paper (group x magnitude x fairness)
m1gl1 <-
  glmer(
  allData$AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group5 + scale(fairLR) * group5 + scale(totalStake) * group5  + scale(fairLR) * scale(totalStake) * group5 +
    (1 | ID/block),
  family = binomial,
  data = allData,
  nAGQ = 0,
  control = glmerControl(optimizer = "bobyqa"))
stargazer(summary(m1gl1)$coefficients, type = "text", title = "AcceptOffer ~ eappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group5 + scale(fairLR) * group5 + scale(totalStake) * group5  + scale(fairLR) * scale(totalStake) * group5 + (1 | ID/block)", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/NoIndividual/group5Interaction.txt")


tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/NoIndividual/group5Interaction.tiff', 
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(m1gl1, "fairLR", by = c("totalStake", "group5"), at = list(fairLR = c(-2.66,0.22),totalStake = c(8,18)))
plot(lsm, horiz = F) +
  theme(axis.text.x=element_text(angle=90, hjust=1)) +
  facet_grid(.~ group5 + totalStake) +
  ggtitle("total stake * fair * group5")
dev.off()

tiff("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/NoIndividual/group5*UGfair.tiff",
      units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(m1gl1, "fairLR", by = c("group5"), at = list(fairLR = c(-2.66,0.22)))
plot(lsm, horiz = F) +
  facet_grid(.~ group5)
dev.off()
 
tiff("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/NoIndividual/group5*totalStake.tiff",
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(m1gl1, "totalStake", by = ("group5"), at = list(totalStake = c(8, 13,18)))
plot(lsm, horiz = F) +
  theme(axis.text.x=element_text(angle=90, hjust=1)) +
  facet_grid(.~ group5)

 

```

## RT analyses
Screening the alternative models of the level 1 predictors. The models include all interaction effect.
```{r}
rt1 <- lmer(
  Stimuli_RT ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + ReappraisalDirection *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4 +  (1 |
  ID/block),
  data = allData[allData$Stimuli_RT<5823 & allData$Stimuli_RT>250,])
  summary(rt1)
car::Anova(rt1)

pdf("RTcontext*group.pdf", width=8, height=6)
lsm <- lsmeans::lsmeans(rt1, "ReappraisalDirection", by = "group4")
plot(lsm, horiz = F)
dev.off()
pdf("RTfair*group.pdf", width=8, height=6)
lsm <- lsmeans::lsmeans(rt1, "fairLR", by = "group4", at = list(fairLR = c(-2.66,-1.22,0.22)))
plot(lsm, horiz = F)
dev.off()
pdf("RTstake*group.pdf", width=8, height=6)
lsm <- lsmeans::lsmeans(rt1, "totalStake", by = "group4", at = list(totalStake = c(8, 13,18)))
plot(lsm, horiz = F)
dev.off()

save.image("ouput.RData")
```

## KE's code
# level1 + level2 with groups (baseline, empathy, resources, reputation)
```{r main model}
#################
# AD: sorry, I could not get through the code below -- all we needed is to split the punishment condition into 2
# and rerun main analysis (but without the 3-way interaction, given the number of parameters)

allData$ReappraisalDirectionResourcesRep <- as.character(allData$PunishingType)
allData$ReappraisalDirectionResourcesRep <- as.factor(dplyr::recode(allData$ReappraisalDirectionResourcesRep, na = 'empathy'))
# sanity check
test <- allData[,c("ReappraisalDirection","PunishingType","ReappraisalDirectionResourcesRep")]
View(test)

# add lagged choice for better model convergence
allData$Trial_Number <- as.integer(allData$Trial_Number)

allData = allData %>% as_tibble %>% arrange(ID, block, Trial_Number)

allDataL = allData %>% arrange(ID, block, Trial_Number) %>% group_by(ID) %>% 
  mutate(
    AcceptOffer_lag = lag(AcceptOffer),
    RT_lag = lag(Stimuli_RT)
    ) %>% ungroup()
sanity_test <- allData[,c("ID", "Trial_Number",   "AcceptOffer","Stimuli_RT")]
View(sanity_test)

lag_test <- allDataL[,c("ID", "Trial_Number",  "block", "AcceptOffer","AcceptOffer_lag","Stimuli_RT", "RT_lag")]
View(lag_test)



# m1gPun is no difference between m1gPun1 (adding pairwise totalStake*group).
m1gPun <-glmer(
  AcceptOffer ~ AcceptOffer_lag + 
    ReappraisalDirectionResourcesRep * scale(fairLR) + 
    ReappraisalDirectionResourcesRep * scale(totalStake) + 
    ReappraisalDirectionResourcesRep * group4 +
    scale(fairLR) * group4 + (1 | ID/block),
  family = binomial,
  data = allDataL,
  control=glmerControl(optCtrl=list(maxfun=1e6), optimizer = "bobyqa"))

stargazer(m1gPun, digits = 2, type = "text", title = "AcceptOffer ~ AcceptOffer lag + ReappraisalDirectionResourcesRep * scale(fairLR) + ReappraisalDirectionResourcesRep * scale(totalStake) + ReappraisalDirectionResourcesRep * group4 + scale(fairLR) * group4 + (1 | ID/block)", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/NoIndividual/group4InteractionPun.txt")
 
write.csv(round(summary(m1gPun)$coefficients, 2), "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/NoIndividual/group4InteractionPun.csv")

         
m1gPunNolag <-glmer(
  AcceptOffer ~ 
    ReappraisalDirectionResourcesRep * scale(fairLR) + 
    ReappraisalDirectionResourcesRep * scale(totalStake) + 
    ReappraisalDirectionResourcesRep * group4 +
    scale(fairLR) * group4 + (1 | ID/block),
  family = binomial,
  data = allData,
  control=glmerControl(optCtrl=list(maxfun=1e6), optimizer = "bobyqa"))

tiff("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/NoIndividual/UGcontext*group4.tiff", units="in", height = 5, width = 12, res=300)
lsm <- lsmeans(m1gPun, "ReappraisalDirectionResourcesRep", by = "group4")
lsmDf <- lsm[1:16]
lsmDf <- as.data.frame(lsmDf)
lsmDf <- subset(lsmDf, lsmDf$ReappraisalDirectionResourcesRep != "baseline")
lsmDf$ReappraisalDirectionResourcesRep <- factor(lsmDf$ReappraisalDirectionResourcesRep)

ggplot(lsmDf, aes(ReappraisalDirectionResourcesRep, lsmean)) +
  geom_errorbar(aes(ymin = lsmean - SE, ymax = lsmean + SE), width = .1,
                position=position_dodge(.1)) +
  geom_point() +
  xlab("Reappraisal Context") +
  ylab("Least Squares Mean") +
  theme_bw(base_size = 14) +
  theme(panel.spacing = unit(2, "lines")) +
  facet_grid(~ group4) +
  scale_x_discrete(labels = c("Empathy", "Reputation", "Resources"), expand=c(0,0.3)) +
  theme(axis.title.x = element_text(margin = margin(t = 15)),
        axis.title.y = element_text(margin = margin(r = 15)))
dev.off()


tiff("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/NoIndividual/UGfair*group4.tiff",
      units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(m1gPun, "fairLR", by = "group4", at = list(fairLR = c(-2.66,-1.22,0.22)))
plot(lsm, horiz = F) +
  facet_grid(~group4)
dev.off() 

tiff("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/NoIndividual/UGstake*group4.tiff",
      units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(m1gPun, "totalStake", by = "group4", at = list(totalStake = c(8, 13,18)))
plot(lsm, horiz = F) +
  facet_grid(~group4)
dev.off() 

tiff("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/NoIndividual/UGcontext*totalStake.tiff", units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(m1gPun, "totalStake", by = "ReappraisalDirectionResourcesRep", at = list(totalStake = c(8, 13,18)))
plot(lsm, horiz = F) +
  facet_grid(~ ReappraisalDirectionResourcesRep)
dev.off()

tiff("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/NoIndividual/UGfair*totalStake.tiff", units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(m1gPun, "totalStake", by = "fairLR", at = list(totalStake = c(8, 13,18),
                                                              fairLR = c(-2.66,-1.22,0.22)))
plot(lsm, horiz = F) +
  facet_grid(~ fairLR)
dev.off()

tiff("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/NoIndividual/UGcontext*UGfair.tiff", units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(m1gPun, "fairLR", by = "ReappraisalDirectionResourcesRep", at = list(fairLR = c(-2.66,-1.22,0.22)))
plot(lsm, horiz = F) +
  facet_grid(~ ReappraisalDirectionResourcesRep)
dev.off()
m1gPun1 <-glmer(
  AcceptOffer ~ AcceptOffer_lag + 
    ReappraisalDirectionResourcesRep * scale(fairLR) + 
    ReappraisalDirectionResourcesRep * scale(totalStake) + 
    ReappraisalDirectionResourcesRep * group4 +
    scale(fairLR) * group4 +
    scale(totalStake) * group4 + (1 | ID/block),
  family = binomial,
  data = allDataL,
  control=glmerControl(optCtrl=list(maxfun=1e6), optimizer = "bobyqa"))

car::Anova(m1gPun)
anova(m1gPun,m1gPun1)

# try the 3 way interaction
# the 3 way interaction is no significant difference with the pair wise interaction model.
m3gPun <-glmer(
  AcceptOffer ~ AcceptOffer_lag + 
    ReappraisalDirectionResourcesRep * scale(fairLR) * scale(totalStake) +
    ReappraisalDirectionResourcesRep * group4 + 
    scale(fairLR) * group4 + 
    scale(totalStake) * group4 +  (1 | ID/block),
  family = binomial,
  data = allDataL,
  control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))
stargazer(summary(m3gPun)$coefficient, type = "text")
write.csv(round(summary(m3gPun)$coefficients, 2), "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/NoIndividual/group4InteractionPun3.csv")

anova(m1gPun, m3gPun)
opt <- all_fit(m3gPun)

AcceptOffer ~ ReappraisalDirection * scale(fairLR) * scale(totalStake) + 
  ReappraisalDirection * group4 + 
  scale(fairLR) * group4 + 
  scale(totalStake) * group4 +  (1 | ID/block)

# reaction time
rt1Pun <- lmer(Stimuli_RT ~  ReappraisalDirectionResourcesRep * scale(fairLR) + ReappraisalDirectionResourcesRep * scale(totalStake) + ReappraisalDirectionResourcesRep *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4  +  (1 |
  ID/block),
  data = allData[allData$Stimuli_RT<5823 & allData$Stimuli_RT>250,])
car::Anova(rt1Pun)
stargazer(summary(rt1Pun)$coefficients, type = "text", title = "Stimuli_RT ~  ReappraisalDirectionResourcesRep * scale(fairLR) + ReappraisalDirectionResourcesRep * scale(totalStake) + ReappraisalDirectionResourcesRep *
  group4 + scale(fairLR) * group4 + scale(totalStake) * group4  +  (1 |
  ID/block)", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/NoIndividual/RTgroup4.txt")

jpeg("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/NoIndividual/RTgroup4.jpg")
lsm <- lsmeans(rt1Pun, "ReappraisalDirectionResourcesRep", by = "group4")
plot(lsm, horiz = F) +
  theme(axis.text = element_text(angle = 90, hjust = 1)) +
  facet_grid(~group4)
dev.off()


# end of Alex's code
##################
stargazer(m1gPun, type = "text", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/NoIndividual/group4Interaction.tex")

stargazer(m1gPun, 
          dep.var.caption = "Accept Offer",
          out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/NoIndividual/group4InteractionPun.tex")

stargazer(m1gPunNolag, type = "text", digits = 2)

```

```{r punishType covariate}
allData$ReappraisalDirectionResourcesRep <- as.character(allData$PunishingType)
allData$ReappraisalDirectionResourcesRep <- as.factor(dplyr::recode(allData$ReappraisalDirectionResourcesRep, na = 'empathy'))
# sanity check
test <- allData[,c("ReappraisalDirection","PunishingType","ReappraisalDirectionResourcesRep")]
View(test)

# add lagged choice for better model convergence
allData$Trial_Number <- as.integer(allData$Trial_Number)

allData = allData %>% as_tibble %>% arrange(ID, block, Trial_Number)

allDataL = allData %>% arrange(ID, block, Trial_Number) %>% group_by(ID) %>% 
  mutate(
    AcceptOffer_lag = lag(AcceptOffer),
    RT_lag = lag(Stimuli_RT)
    ) %>% ungroup()
sanity_test <- allData[,c("ID", "Trial_Number",   "AcceptOffer","Stimuli_RT")]
View(sanity_test)

lag_test <- allDataL[,c("ID", "Trial_Number",  "block", "AcceptOffer","AcceptOffer_lag","Stimuli_RT", "RT_lag")]
View(lag_test)

newdataPunish <- allData[, c("AcceptOffer", "ReappraisalDirectionResourcesRep", "fairLR", "totalStake",
                       "group4", "EXIT", "EDUCATION", "IIP15INTSEN",
                       "Gender", "IncomePerCapita", "BIS_NONPLAN", "IIP15INTAMBV",
                       "ID", "block", "DRS", "HRSD_NO_SUI")]
      
newdataPunish$ID <- as.factor(newdata$ID)
newdataPunish$block <- as.factor(newdata$block)
newdataPunish$Gender <- as.factor(newdata$Gender)
newdataPunish$group4 <- as.factor(newdata$group4)
newdataPunish$AcceptOffer <- as.factor(newdata$AcceptOffer)

newdataPunish[, c("fairLR", "totalStake","EXIT", "EDUCATION", "IIP15INTSEN","IncomePerCapita", "BIS_NONPLAN", "IIP15INTAMBV", "DRS", "HRSD_NO_SUI")] <- 
  scale(newdata[, c("fairLR", "totalStake","EXIT", "EDUCATION", "IIP15INTSEN","IncomePerCapita", "BIS_NONPLAN", "IIP15INTAMBV", "DRS", "HRSD_NO_SUI")])

mpun1 <-
  glmer(
    AcceptOffer ~ ReappraisalDirectionResourcesRep * fairLR *  
    totalStake + ReappraisalDirectionResourcesRep * group4 + fairLR *  
    group4 + totalStake * group4 + 
      ReappraisalDirectionResourcesRep *  EXIT +
      EDUCATION * group4 * ReappraisalDirectionResourcesRep +  
      IIP15INTSEN * group4 * ReappraisalDirectionResourcesRep + 
      Gender * ReappraisalDirectionResourcesRep +  
      ReappraisalDirectionResourcesRep * DRS * group4 + 
      HRSD_NO_SUI *ReappraisalDirectionResourcesRep*group4 +
      (1 | ID/block),
    family = binomial,
  data = na.omit(newdataPunish),
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

stargazer(mpun1, type = "text", title = "AcceptOffer ~ ReappraisalDirectionResourcesRep * fairLR *  totalStake + ReappraisalDirectionResourcesRep * group4 + fairLR * group4 + totalStake * group4 + ReappraisalDirectionResourcesRep *  EXIT + EDUCATION * group4 * ReappraisalDirectionResourcesRep + IIP15INTSEN * group4 * ReappraisalDirectionResourcesRep + Gender * ReappraisalDirectionResourcesRep + (1 | ID/block)",
          out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/individualCharacterModel.txt")


tiff("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/UGcontext*group4.tiff",
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(mpun1, "ReappraisalDirectionResourcesRep", by = "group4")
plot(lsm, horiz = F) +
    facet_grid(~ group4)
dev.off()

tiff("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/UGfair*group4.tiff",
      units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(mpun1, "fairLR", by = "group4", at = list(fairLR = c(-2.66,-1.22,0.22)))
plot(lsm, horiz = F) +
  facet_grid(~group4)
dev.off() 

tiff("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/totalStake*group4.tiff",
      units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(mpun1, "totalStake", by = "group4", at = list(totalStake = c(8, 13,18)))
plot(lsm, horiz = F) +
  facet_grid(~group4)
dev.off() 

lsm <- lsmeans(mc7, "ReappraisalDirection", by = c("EXIT", "group4"), at = list(EXIT = c(5, 10, 15)))
tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/main/UGcontext*EXIT*group4.tiff', 
     units="in", height = 8, width = 10, res=300)
plot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(.~ EXIT + group4)  + ggtitle("UGcontext*EXIT*group4")
dev.off()

lsm <- lsmeans(mpun1, "ReappraisalDirectionResourcesRep", by = c("DRS", "group4"), at = list(DRS = c(130, 135, 140)))
tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/UGcontext*DRS*group4.tiff', 
     units="in", height = 8, width = 10, res=300)
plot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(.~ DRS + group4)  + ggtitle("UGcontext*DRS*group4")
dev.off()

lsm <- lsmeans(mpun1, "ReappraisalDirectionResourcesRep", by = c("HRSD_NO_SUI", "group4"), at = list(HRSD_NO_SUI = c(5, 15, 25)))
tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/UGcontext*HRSD_NO_SUI*group4.tiff', 
     units="in", height = 8, width = 10, res=300)
plot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(.~ HRSD_NO_SUI + group4)  + ggtitle("UGcontext*HRSD_NO_SUI*group4")
dev.off()


lsm <- lsmeans(mpun1, "ReappraisalDirectionResourcesRep", by = c("IIP15INTSEN", "group4"), at = list(IIP15INTSEN = c(3,5,10)))
tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/UGcontext*IIP15INTSEN*group4.tiff', 
     units="in", height = 8, width = 10, res=300)
plot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(.~ IIP15INTSEN + group4)  + ggtitle("UGcontext*IIP15INTSEN*group4")
dev.off()


lsm <- lsmeans(mpun1, "ReappraisalDirectionResourcesRep", by = c("EDUCATION", "group4"), at = list(EDUCATION = c(13,15,16)))
tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/UGcontext*EDUCATION*group4.tiff', 
     units="in", height = 8, width = 10, res=300)
plot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(.~ EDUCATION + group4)  + ggtitle("UGcontext*EDUCATION*group4")
dev.off()


tiff("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/UGcontext*gender.tiff",
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(mpun1, "Gender", by = "ReappraisalDirectionResourcesRep")
plot(lsm, horiz = F) +
  facet_grid(~ ReappraisalDirectionResourcesRep)
dev.off()
?lag

```


```{r, lethality group5 interaction}
m1gPunG5 <-glmer(
  AcceptOffer ~ AcceptOffer_lag + 
    ReappraisalDirectionResourcesRep * scale(fairLR) + 
    ReappraisalDirectionResourcesRep * scale(totalStake) + 
    ReappraisalDirectionResourcesRep * group5 +
    scale(fairLR) * group5 + (1 | ID/block),
  family = binomial,
  data = allDataL,
  control=glmerControl(optCtrl=list(maxfun=1e6), optimizer = "bobyqa"))

stargazer(summary(m1gPunG5)$coefficients, type = "text", title = "AcceptOffer ~ ReappraisalDirectionResourcesRep * scale(fairLR) + ReappraisalDirectionResourcesRep * scale(totalStake) + ReappraisalDirectionResourcesRep *
  group5 + scale(fairLR) * group5 + (1 | ID/block)", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/NoIndividual/group5InteractionPun1.txt")


jpeg("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/NoIndividual/group5*Pun.jpg")
lsm <- lsmeans(m1gPunG5, "ReappraisalDirectionResourcesRep", by = "group5")
plot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(~ group5)
dev.off()

jpeg("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/NoIndividual/group5*fair.jpg")
lsm <- lsmeans(m1gPunG5, "fairLR", by = "group5", at = list(fairLR = c(-2.66,-1.22,0.22)))
plot(lsm, horiz = F) +
  facet_grid(~group5)
dev.off() 

jpeg("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/NoIndividual/Pun*fair.jpg")
lsm <- lsmeans(m1gPunG5, "fairLR", by = "ReappraisalDirectionResourcesRep", at = list(fairLR = c(-2.66,-1.22,0.22)))
plot(lsm, horiz = F) +
  facet_grid(~ ReappraisalDirectionResourcesRep)
dev.off()

jpeg("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/NoIndividual/Pun*totalStake.jpg")
lsm <- lsmeans(m1gPunG5, "totalStake", by = "ReappraisalDirectionResourcesRep", at = list(totalStake = c(8, 13,18)))
plot(lsm, horiz = F) +
  facet_grid(~ ReappraisalDirectionResourcesRep)
dev.off()

lsm <- lsmeans(m1gPunG5, "AcceptOffer_lag")
plot(lsm, horiz = F)
dev.off()


```

```{r control MMSE EXIT}
# THE FOLLOWING CODES ARE CONTROLLING INDIVIDUAL VARS
# no missing values
# control for MMSE with (1 | ID)

m1gPun_m1 <-glmer(
  AcceptOffer ~ AcceptOffer_lag + 
    ReappraisalDirectionResourcesRep * scale(fairLR) + 
    ReappraisalDirectionResourcesRep * scale(totalStake) + 
    ReappraisalDirectionResourcesRep * group4 +
    scale(fairLR) * group4 + 
    ReappraisalDirectionResourcesRep*scale(MMSE)+ (1 | ID/block),
  family = binomial,
  data = allDataL,
  control=glmerControl(optCtrl=list(maxfun=1e6), optimizer = "bobyqa"))

stargazer(modelPun1_mg, type = "text")
summary(modelPun1_mg)
car::Anova(modelPun1_mg, type = 'III')
jpeg("punishType*MMSE_ind.jpg")
lsm <- lsmeans(modelPun1_mg, "PunishingType", by = "MMSE", at = list(MMSE = c(26,28,30)))
plot(lsm, horiz = F)
dev.off()

# PunishingType*scale(MMSE)*group4
m1gPun_E1 <-glmer(
  AcceptOffer ~ AcceptOffer_lag + 
    ReappraisalDirectionResourcesRep * scale(fairLR) + 
    ReappraisalDirectionResourcesRep * scale(totalStake) + 
    ReappraisalDirectionResourcesRep * group4 +
    scale(fairLR) * group4 + 
    ReappraisalDirectionResourcesRep*scale(EXIT)*group4+ (1 | ID/block),
  family = binomial,
  data = allDataL,
  control=glmerControl(optCtrl=list(maxfun=1e6), optimizer = "bobyqa")) 

stargazer(m1gPun_E1, type = "text", title = "AcceptOffer ~ AcceptOffer ~ AcceptOffer_lag + ReappraisalDirectionResourcesRep * scale(fairLR) + ReappraisalDirectionResourcesRep * scale(totalStake) + ReappraisalDirectionResourcesRep * group4 + scale(fairLR) * group4 + ReappraisalDirectionResourcesRep*scale(EXIT)*group4+ (1 | ID/block))",out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/punishType*group4*EXIT.txt")

lsm <- lsmeans(m1gPun_E1, "ReappraisalDirectionResourcesRep", by = c("EXIT", "group4"), at = list(EXIT = c(5, 10, 15)))
anova(modelPun3_mg, modelPun2_mg)
```
```{r gender}
m1gPun_Gen2 <-glmer(
  AcceptOffer ~ AcceptOffer_lag + 
    ReappraisalDirectionResourcesRep * scale(fairLR) + 
    ReappraisalDirectionResourcesRep * scale(totalStake) + 
    ReappraisalDirectionResourcesRep * group4 +
    scale(fairLR) * group4 + 
    ReappraisalDirectionResourcesRep*Gender*group4+ (1 | ID/block),
  family = binomial,
  data = allDataL,
  control=glmerControl(optCtrl=list(maxfun=1e6), optimizer = "bobyqa")) 

stargazer(m1gPun_Gen1, type = "text", title = "AcceptOffer ~ AcceptOffer ~ AcceptOffer_lag + ReappraisalDirectionResourcesRep * scale(fairLR) + ReappraisalDirectionResourcesRep * scale(totalStake) + ReappraisalDirectionResourcesRep * group4 + scale(fairLR) * group4 + ReappraisalDirectionResourcesRep*Gender+ (1 | ID/block))",out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/punishType*Gender.txt")

tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/punishType*Gender.tiff', 
     units="in", height = 8, width = 10, res=300)
lsm <- lsmeans(m1gPun_Gen1, "ReappraisalDirectionResourcesRep", 
               by = c("Gender"))
print(lsm)
plot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(.~ Gender)  + ggtitle("Gender")
dev.off()
```

```{r education}
m1gPun_Edu <-glmer(
  AcceptOffer ~ AcceptOffer_lag + 
    ReappraisalDirectionResourcesRep * scale(fairLR) + 
    ReappraisalDirectionResourcesRep * scale(totalStake) + 
    ReappraisalDirectionResourcesRep * group4 +
    scale(fairLR) * group4 + 
    ReappraisalDirectionResourcesRep*scale(EDUCATION)*group4+ (1 | ID/block),
  family = binomial,
  data = allDataL,
  control=glmerControl(optCtrl=list(maxfun=1e6), optimizer = "bobyqa")) 

stargazer(m1gPun_Edu, type = "text", title = "AcceptOffer ~ AcceptOffer ~ AcceptOffer_lag + ReappraisalDirectionResourcesRep * scale(fairLR) + ReappraisalDirectionResourcesRep * scale(totalStake) + ReappraisalDirectionResourcesRep * group4 + scale(fairLR) * group4 + ReappraisalDirectionResourcesRep*scale(EDUCATION)*group4+ (1 | ID/block))",out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/punishType*Edu*group4.txt")



```

```{r IIP15INTSEN}
m1gPun_IIPSEN <-glmer(
  AcceptOffer ~ AcceptOffer_lag + 
    ReappraisalDirectionResourcesRep * scale(fairLR) + 
    ReappraisalDirectionResourcesRep * scale(totalStake) + 
    ReappraisalDirectionResourcesRep * group4 +
    scale(fairLR) * group4 + 
    ReappraisalDirectionResourcesRep*scale(IIP15INTSEN)*group4+ (1 | ID/block),
  family = binomial,
  data = allDataL,
  control=glmerControl(optCtrl=list(maxfun=1e6), optimizer = "bobyqa")) 

stargazer(m1gPun_IIPSEN, type = "text", title = "AcceptOffer ~ AcceptOffer ~ AcceptOffer_lag + ReappraisalDirectionResourcesRep * scale(fairLR) + ReappraisalDirectionResourcesRep * scale(totalStake) + ReappraisalDirectionResourcesRep * group4 + scale(fairLR) * group4 + ReappraisalDirectionResourcesRep*scale(IIP15INTSEN)*group4+ (1 | ID/block))",out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/punishType*IIP15INTSEN*group4.txt")


```

```{r, control lethality group5}
# PunishingType*scale(MMSE)
modelPun4_mg <-
  glmer(
  punishMaster$AcceptOffer ~ PunishingType * scale(fairLR) * scale(totalStake) +
    PunishingType*
    group5 + scale(fairLR) * group5 + scale(totalStake) * group5
    +PunishingType*scale(MMSE) + (1 | ID/block),
    family = binomial,
    data = punishMaster,
    control = glmerControl(optimizer = "bobyqa"))
stargazer(modelPun4_mg, type = "text", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/punishType*group5*MMSE_ind.txt")
lsm <- lsmeans(modelPun4_mg, "PunishingType", by = c("MMSE", "group5"), at = list(MMSE = c(26,28,30)))
jpeg("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/punishType*group5*MMSE_ind.jpg")
plot(lsm, horiz = F) +
  theme(axis.text.x=element_text(angle=90, hjust=1))+
  facet_grid(~ MMSE + group5) 

```

```{r, individual vars group4}
VarLoopDF <- punishMaster[, c("MMSE", "PROTECT2AGE", "GENDERTEXT", "IncomePerCapita", "HRSD_NO_SUI", "EDUCATION", "BIS_NONPLAN", "urgency", "IIP15INTAMBV", "IIP15INTSEN", "IIP15AGRESS", "IRI_EMPATHETIC_CONCERN")]

# scale punish df individual factors, rm categorical vars and missing value vars
scaleVarLs <- scale(VarLoopDF[, c("MMSE", "PROTECT2AGE", "IncomePerCapita", "HRSD_NO_SUI", "EDUCATION")])

#scaleVarLsDF <- scale(scaleVarLs)
punishMasterScale <- punishMaster
punishMasterScale[, c("MMSE", "PROTECT2AGE", "IncomePerCapita", "HRSD_NO_SUI", "EDUCATION")] <- scaleVarLs

# variables list without/with the missing value variables
varlist_complete <- list("MMSE", "EDUCATION", "IncomePerCapita", "PROTECT2AGE", "HRSD_NO_SUI")
varlist_missing <- list('BIS_NONPLAN', 'IIP15AGRESS','IIP15INTSEN', 'IIP15INTAMBV', 'urgency', "IRI_EMPATHETIC_CONCERN")

## PunishingType*vars
### output models
modelPun1_2way <- lapply(varlist_missing, function(individualFactor) {
  models <- glmer(substitute(AcceptOffer ~ PunishingType * scale(fairLR) * scale(totalStake) +
    PunishingType*group4 + scale(fairLR) * group4 + scale(totalStake) * group4
    + PunishingType*i + (1 | ID/block), 
    list(i = as.name(individualFactor))),
    data = punishMasterScale,
    family = binomial,
    control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
    return(stargazer(models, type = "text", title = paste("AcceptOffer ~ PunishingType * fairLR * totalStake +  PunishingType*group4 + fairLR * group4 + totalStake * group4 + PunishingType*", individualFactor, "+ (1 | ID/block)"), out = paste("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/punishType*", individualFactor, ".txt")))
})

### output models graphs
pltFunPun1_2way <- lapply(varlist_complete, function(individualFactor) {
  models <- glmer(substitute(AcceptOffer ~ PunishingType * scale(fairLR) * scale(totalStake) +
    PunishingType*group4 + scale(fairLR) * group4 + scale(totalStake) * group4
    + PunishingType*i + (1 | ID/block), 
    list(i = as.name(individualFactor))),
    data = punishMasterScale,
    family = binomial,
    control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))

    vars <- (punishMasterScale[, individualFactor])
    print(class(vars))
    intervalLength <- ifelse(class(vars) == "numeric", (max(vars) - min(vars))/5, list(unique(vars)))
    print(intervalLength)
    lvls <- ifelse(class(vars) == "numeric", list(seq(from=min(vars), to=max(vars)), by = intervalLength), intervalLength)
    jpeg(paste("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/punishType*",
               individualFactor,".jpg"))
    lsm <- lsmeans(models, "PunishingType", by = c(individualFactor, "group4"), at = list(individualFactor = lvls)) 
    plot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(~ individualFactor+group4) +
    ggtitle(paste("AcceptOffer ~ PunishingType * fairLR * totalStake +
    PunishingType*group4 + fairLR * group4 + totalStake * group4
    + PunishingType*",individualFactor, "+ (1 | ID/block)"))
    dev.off()
    
})

## PunishingType*vars*group4
### output models
modelPun1_3way <- lapply(varlist_missing, function(individualFactor) {
  models <- glmer(substitute(AcceptOffer ~ PunishingType * scale(fairLR) * scale(totalStake) +
    PunishingType*group4 + scale(fairLR) * group4 + scale(totalStake) * group4
    + PunishingType*group4*i + (1 | ID/block), 
    list(i = as.name(individualFactor))),
    data = punishMasterScale,
    family = binomial,
    control = glmerControl(optimizer = "bobyqa"))
    return(stargazer(models, type = "text", title = paste("AcceptOffer ~ PunishingType * fairLR * totalStake +  PunishingType*group4 + fairLR * group4 + totalStake * group4 + PunishingType*group4*", individualFactor, "+ (1 | ID/block)"), out = paste("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/punishType*group4*", individualFactor, ".txt")))
})

### output models graphs
pltFunPun1_3way <- lapply(varlist_complete, function(individualFactor) {
  models <- glmer(substitute(AcceptOffer ~ PunishingType * scale(fairLR) * scale(totalStake) +
    PunishingType*group4 + scale(fairLR) * group4 + scale(totalStake) * group4
    + PunishingType*group4*i + (1 | ID/block), 
    list(i = as.name(individualFactor))),
    data = punishMasterScale,
    family = binomial,
    control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
    
    print(individualFactor)
    vars <- (punishMasterScale[, individualFactor])
    print(vars)
    print(class(vars))
    #intervalLength <- ifelse(class(vars) == "numeric", (max(vars) - min(vars))/2, list(unique(vars)))
    #print(intervalLength)
    lvls <- ifelse(class(vars) == "numeric", list(seq(min(vars), max(vars), length.out = 3)), list(unique(vars)))
    print(lvls)
    jpeg(file = paste("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/punishType*group4*",individualFactor,".jpg"))
    lsm <- lsmeans(models, "PunishingType", by = c(individualFactor, "group4"), at = list(individualFactor = lvls)) 
    plt <- plot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(as.formula(paste(". ~", paste(individualFactor, "+ group4")))) +
    ggtitle(paste("AcceptOffer ~ PunishingType * fairLR * totalStake +
    PunishingType*group4 + fairLR * group4 + totalStake * group4
    + PunishingType*group4*",individualFactor, "+ (1 | ID/block)"))
    dev.off()
    print(plt)
    return(plt)
})


```

```{r, individual vars group5}
## PunishingType*vars*group5
### output models
modelPun2_3way <- lapply(varlist_complete, function(individualFactor) {
  models <- glmer(substitute(PunishingType * scale(fairLR) * scale(totalStake) +
    PunishingType*group5 + scale(fairLR) * group5 + scale(totalStake) * group5
    + PunishingType*group5*i + (1 | ID/block), 
    list(i = as.name(individualFactor))),
    data = punishMasterScale,
    family = binomial,
    control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
    return(stargazer(models, type = "text", title = paste("AcceptOffer ~ PunishingType * fairLR * totalStake +  PunishingType*group5 + fairLR * group5 + totalStake * group5 + PunishingType*group5*", x, "+ (1 | ID/block)"), out = paste("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/punishType*group5*", individualFactor, ".txt")))
})

### output models graphs
pltFunPun2_3way <- lapply(varlist, function(individualFactor) {
  models <- glmer(substitute(PunishingType * scale(fairLR) * scale(totalStake) +
    PunishingType*group5 + scale(fairLR) * group5 + scale(totalStake) * group5
    + PunishingType*group5*i + (1 | ID/block), 
    list(i = as.name(individualFactor))),
    data = punishMasterScale,
    family = binomial,
    control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))

    vars <- (punishMaster[, individualFactor])
    print(class(vars))
    intervalLength <- ifelse(class(vars) == "numeric", (max(vars) - min(vars))/5, list(unique(vars)))
    print(intervalLength)
    lvls <- ifelse(class(vars) == "numeric", seq(from=min(vars), to=max(vars), by = intervalLength), intervalLength)
    jpeg(paste("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/punishType/punishType*group5*",
               individualFactor,".jpg"))
    lsm <- lsmeans(models, "PunishingType", by = c(individualFactor, "group5"), at = list(individualFactor = lvls)) 
    plt <- plot(lsm, horiz = F) +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(~ individualFactor+group5) +
    ggtitle(paste("AcceptOffer ~ PunishingType * fairLR * totalStake +
    PunishingType*group5 + fairLR * group5 + totalStake * group5
    + PunishingType*group5*",individualFactor, "+ (1 | ID/block)"))
    dev.off()
    return(plt)
})

```

# Ke's codes on emotional reactivity
# post-survey analysis 
```{r emotion clean data}
# emotion reactivity within the 3 categories of quesions
emoRating$ReappraisalDirection <- recode(emoRating$ReappraisalDirection, "1"= "punish", "2" = "empathy")
emoRating$PunishingType <- as.character(emoRating$PunishingType)
emoRating$PunishingType <- as.factor(recode(emoRating$PunishingType, na = "empathy"))
levels(emoRating$group4)[levels(emoRating$group4) == "control"] <- "Control"
levels(emoRating$group4)[levels(emoRating$group4) == "attempter"] <- "Attempter"
levels(emoRating$group4)[levels(emoRating$group4) == "ideator"] <- "Ideator"
levels(emoRating$group4)[levels(emoRating$group4) == "depression"] <- "Depression"


unfair <- subset(emoRating, emoRating$Q_type == "unfair")
sympathy <- subset(emoRating, emoRating$Q_type == "sympathy")
anger <- subset(emoRating, emoRating$Q_type == "anger")

empathyDF <- subset(emoRating, emoRating$ReappraisalDirection == "empathy")
punishDF <- subset(emoRating, emoRating$ReappraisalDirection == "punish")
resourcesDF <- subset(emoRating, emoRating$PunishingType == "resources")
reputationDF <- subset(emoRating, emoRating$PunishingType == "reputation")

# jpeg('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/reactivity/NoIndividual/boxGroup4.jpg')
# boxplot(emoRating$Rating ~ emoRating$group4, main = "Emotion reactivity")
# dev.off()
# jpeg('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/reactivity/NoIndividual/boxPunishType.jpg')
# boxplot(emoRating$Rating ~ emoRating$PunishingType, main = "Emotion reactivity")
# dev.off()
# jpeg('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/reactivity/NoIndividual/boxQ_type.jpg')
# boxplot(emoRating$Rating ~ emoRating$Q_type, main = "Emotion reactivity")
# dev.off()
# boxplot(emoRating$Rating ~ emoRating$ReappraisalDirection, main = "Emotion reactivity")
```

```{r post survey HLM?}
## HLM necessary?
interceptOnly <- glm(Rating ~ 1, family = gaussian, data = reactivity)
print(summary(interceptOnly))

### Null model: random intercept only
randomInterceptOnly <- glmer(Rating~ 1 + (1|ID), data = reactivity, family = gaussian)
print(summary(randomInterceptOnly))

ICC_model <- function(modelName) {
  tau_null <- as.numeric(lapply(summary(modelName)$varcor, diag))
  sigma_null <- as.numeric(attr(summary(modelName)$varcor, "sc")^2)
  ICC_null <- tau_null/(tau_null + sigma_null)
  return(ICC_null)
}
cat("ICC is", ICC_model(randomInterceptOnly))
```
HLM is needed.

```{r, reactivity model}
# reactivity of each question: unfairness, sympathy, and anger under reppraisal direction
mFair <- lmer(scale(Rating) ~ PunishingType*group4 + (1|ID), data = unfair)
tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/reactivity/NoIndividual/QfairnessContext.tiff',
      units="in", height = 5, width = 12, res=300)
lsm <- lsmeans(mFair, "PunishingType", by="group4")
lsmDf <- lsm[1:12]
lsmDf <- as.data.frame(lsmDf)
lsmDf$PunishingType <- factor(lsmDf$PunishingType)
ggplot(lsmDf, aes(PunishingType, lsmean)) +
  geom_errorbar(aes(ymin = lsmean - SE, ymax = lsmean + SE), width = .1,
                position=position_dodge(.1)) +
  geom_point() +
  xlab("Reappraisal Context") +
  ylab("Least Squares Mean") +
  theme_bw(base_size = 14) +
  theme(panel.spacing = unit(2, "lines"),
        strip.text.x = element_text(size = 16)) +
  facet_grid(~ group4) +
  scale_x_discrete(labels = c("Empathy", "Reputation", "Resources"), expand=c(0.05,0.40)) +
  theme(axis.title.x = element_text(margin = margin(t = 15)),
        axis.title.y = element_text(margin = margin(r = 15)))
dev.off()

stargazer(summary(mFair)$coefficients, type = "text", 
          title = "Unfairness:scale(Rating) ~ PunishingType*group4 + (1|ID)", 
          out = '/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/reactivity/NoIndividual/Qfairness.txt')

msympathy <- lmer(scale(Rating) ~ PunishingType*group4 + (1|ID), data = sympathy)
tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/reactivity/NoIndividual/QsympathyN.jpg',
      units="in", height = 5, width = 12, res=300)
lsm <- lsmeans(msympathy, "PunishingType", by="group4")
lsmDf <- lsm[1:12]
lsmDf <- as.data.frame(lsmDf)
lsmDf$PunishingType <- factor(lsmDf$PunishingType)
ggplot(lsmDf, aes(PunishingType, lsmean)) +
  geom_errorbar(aes(ymin = lsmean - SE, ymax = lsmean + SE), width = .1,
                position=position_dodge(.1)) +
  geom_point() +
  xlab("Reappraisal Context") +
  ylab("Least Squares Mean") +
  theme_bw(base_size = 14) +
  theme(panel.spacing = unit(2, "lines"),
        strip.text.x = element_text(size = 16)) +
  facet_grid(~ group4) +
  scale_x_discrete(labels = c("Empathy", "Reputation", "Resources"), expand=c(0.05,0.40)) +
  theme(axis.title.x = element_text(margin = margin(t = 15)),
        axis.title.y = element_text(margin = margin(r = 15)))
dev.off()

stargazer(summary(msympathy)$coefficients, type = "text", title = "Sympathy: scale(Rating) = PunishingType*group4 + (1|ID)",out = '/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/reactivity/NoIndividual/Qsympathy.txt')

manger <- lmer(scale(Rating) ~ PunishingType*group4 + (1|ID), data = anger)
tiff('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/reactivity/NoIndividual/QangerN.jpg',
      units="in", height = 5, width = 12, res=300)
lsm <- lsmeans(manger, "PunishingType", by="group4")
lsmDf <- lsm[1:12]
lsmDf <- as.data.frame(lsmDf)
lsmDf$PunishingType <- factor(lsmDf$PunishingType)
ggplot(lsmDf, aes(PunishingType, lsmean)) +
  geom_errorbar(aes(ymin = lsmean - SE, ymax = lsmean + SE), width = .1,
                position=position_dodge(.1)) +
  geom_point() +
  xlab("Reappraisal Context") +
  ylab("Least Squares Mean") +
  theme_bw(base_size = 14) +
  theme(panel.spacing = unit(2, "lines"),
        strip.text.x = element_text(size = 16)) +
  facet_grid(~ group4) +
  scale_x_discrete(labels = c("Empathy", "Reputation", "Resources"), expand=c(0.05,0.40)) +
  theme(axis.title.x = element_text(margin = margin(t = 15)),
        axis.title.y = element_text(margin = margin(r = 15)))
dev.off()


# Reappraisal = empathy, reputation, resources
m_3type1 <- lmer(scale(Rating) ~ Q_type*group4 + PunishingType * group4 + (1|ID), data = emoRating)
jpeg('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/reactivity/NoIndividual/reactivity_3types.jpg',
     width = 950, height = 480, units = "px", pointsize = 12,
     quality = 75)
lsm <- lsmeans(m_3type1, "PunishingType", by = c("Q_type", "group4"))
plot(lsm, col = emoRating$Q_type,horiz = F) +
  facet_grid( ~ PunishingType + group4) +
  theme(axis.text.x=element_text(angle=90, hjust=1)) 
dev.off()
stargazer(summary(m_3type1)$coefficients, type = "text", title="scale(Rating) ~ Q_type*group4 + PunishingType * group4 + (1|ID)",out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/reactivity/NoIndividual/reactivity_3types.txt")

# Reappraisal = empathy, punish
m_2type <- lmer(scale(Rating) ~ Q_type*group4 + ReappraisalDirection*group4 + (1|ID), data = emoRating)  
jpeg('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/reactivity/NoIndividual/reactivity_2types.jpg',
     width = 950, height = 480, units = "px", pointsize = 12,
     quality = 75)
lsm <- lsmeans(m_2type, "ReappraisalDirection", by = c("Q_type", "group4"))
plot(lsm, horiz = F) +
  facet_grid( ~ ReappraisalDirection + group4) +
  theme(axis.text.x=element_text(angle=90, hjust=1)) 
stargazer(summary(m_2type)$coefficients, type = "text", title="scale(Rating) ~ Q_type*group4 + ReappraisalDirection*group4 + (1|ID)",out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/reactivity/NoIndividual/reactivity_2types.txt")


class(mFair) <- "lmerMod"
class(msympathy) <- "lmerMod"
class(manger) <- "lmerMod"

stargazer(mFair, msympathy, manger, align = T,
          column.labels = c("Fairness", "Sympathy", "Anger"),
          dep.var.labels = "Ratings" ,
          digits = 2,
          covariate.labels = c("Reputation", "Resources", "Control", "Depression",
                               "Ideator", "Reputation  x Control", "Resources x Control",
                               "Reputation x Depression", "Resources x Depression",
                               "Reputation x Ideator", "Resources x Ideator", "Constant"),
          type = "text")
          # out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/reactivity/NoIndividual/emoRating.html")
levels(unfair$PunishingType)
stargazer(manger, type = "text", report = c("vcs*p"), out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/reactivity/NoIndividual/emoRating.html")
summary(manger)$coefficients

```

# control individual factors
The followings are controlling demographics and other questionnaires-based variables.
```{r, MMSE}
mReact4MMSE1 <- lmer(
  scale(Rating) ~ ReappraisalDirection*group4 + scale(MMSE) + (1|ID), data = emoRating)
jpeg('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/rating=group4*Reappraisal_MMSE.jpg')
lsm <- lsmeans(mReact4MMSE1, "ReappraisalDirection", by = c("group4"))
plot(lsm, horiz = F) +
  facet_grid(. ~ group4) +
  ggtitle("MMSE")
dev.off()
mEff <- allEffects(mReact4MMSE1)
plot(mEff, axes = list(y = list(lab = "reactivity")))
summary(mReact4MMSE1)
stargazer(summary(mReact4MMSE1)$coefficients, type = "text", title = "Rating ~ ReappraisalDirection*group4 + MMSE + (1|ID)",
          out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/rating=group4*Reappraisal_MMSE.txt")

mReact4MMSE2 <- lmer(
  scale(Rating) ~ ReappraisalDirection*group4*scale(MMSE) + (1|ID), data = emoRating)
jpeg('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/rating=ReappraisalDirection*group4*MMSE.jpg')
lsm <- lsmeans(mReact4MMSE2, "ReappraisalDirection", by = c("group4"))
plot(lsm, horiz = F, xlab = "reappraisal type") +
  facet_grid(. ~ group4) +
  ggtitle("MMSE")
dev.off()
mEff <- allEffects(mReact4MMSE2)
plot(mEff, axes = list(y = list(lab = "reactivity")))
summary(mReact4MMSE2)
stargazer(summary(mReact4MMSE2)$coefficients, type = "text", title = "Rating ~ ReappraisalDirection*group4*MMSE + (1|ID)",
          out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/rating=ReappraisalDirection*group4*MMSE.txt")

anova(mReact4MMSE1, mReact4MMSE2)

mReact5MMSE1 <- lmer(
  scale(Rating) ~ ReappraisalDirection*group5 + scale(MMSE) + (1|ID), data = emoRating)
jpeg('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/rating=group5*Reappraisal_MMSE.jpg')
lsm <- lsmeans(mReact5MMSE1, "ReappraisalDirection", by = c("group5"))
plot(lsm, horiz = F) +
  facet_grid(. ~ group5) +
  ggtitle("MMSE")
dev.off()
mEff <- allEffects(mReact5MMSE1)
plot(mEff, axes = list(y = list(lab = "reactivity")))
summary(mReact5MMSE1)
stargazer(summary(mReact5MMSE1)$coefficients, type = "text", title = "Rating ~ ReappraisalDirection*group5 + MMSE + (1|ID)",
          out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/rating=group5*Reappraisal_MMSE.txt")

mReact5MMSE2 <- lmer(
  scale(Rating) ~ ReappraisalDirection*group5*scale(MMSE) + (1|ID), data = emoRating)
jpeg('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/rating=ReappraisalDirection*group5*MMSE.jpg')
lsm <- lsmeans(mReact5MMSE2, "ReappraisalDirection", by = c("group5"))
plot(lsm, horiz = F, xlab = "reappraisal type") +
  facet_grid(. ~ group5) +
  ggtitle("MMSE")
dev.off()
mEff <- allEffects(mReact5MMSE2)
plot(mEff, axes = list(y = list(lab = "reactivity")))
summary(mReact5MMSE2)
stargazer(summary(mReact5MMSE2)$coefficients, type = "text", title = "Rating ~ ReappraisalDirection*group5*MMSE + (1|ID)",
          out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/rating=ReappraisalDirection*group5*MMSE.txt")

anova(mReact5MMSE2, mReact5MMSE1)

# group*MMSE*direction is better than two way interaction
```

```{r, individual factors}
VarLoop <- emoRating[, c("MMSE", "PROTECT2AGE", "GENDERTEXT", "IncomePerCapita", "HRSD_NO_SUI", "EDUCATION", "RACETEXT", "DRS", "EXIT", "BIS_NONPLAN", "urgency", "IIP15INTAMBV", "IIP15INTSEN", "IIP15AGRESS", "IRI_EMPATHETIC_CONCERN")]

# scaled emoRating df
#tmp <- sapply(emoRating, is.numeric)
#emoRatingScale <- emoRating
#emoRatingScale[tmp] <- lapply(emoRating[tmp], scale)

scaleVar <- scale(VarLoop[, c("MMSE", "PROTECT2AGE", "IncomePerCapita", "HRSD_NO_SUI", "EDUCATION")])

emoRatingScale <- emoRating
emoRatingScale[, c("MMSE", "PROTECT2AGE", "IncomePerCapita", "HRSD_NO_SUI", "EDUCATION")] <- scaleVar


# group4
## loop through all vars by "rating = ReappraisalDirection*group4*i + (1|ID)"
### output models

mReact4_3way <- lapply(varlist_complete, function(individualFactor){
  models <- lmer(substitute(Rating ~ ReappraisalDirection*group4*i + (1|ID),
                            list(i = as.name(individualFactor))),
                 data = emoRatingScale)
  return(models)
  #return(stargazer(models, type = "text", title = paste("Rating ~ ReappraisalDirection*group4*", individualFactor, "+ (1|ID)"), out =
                     #paste("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/reactivity/ReappraisalDirection*group4*", individualFactor, ".txt")))
})


### output models graphs
pltFun_React4_3way <- lapply(varlist_complete, function(individualFactor) {
  models <- lmer(substitute(Rating ~ ReappraisalDirection*group4*i + (1|ID),
                            list(i = as.name(individualFactor))), data = emoRatingScale)
  
  print(individualFactor)
  vars <- (emoRatingScale[, individualFactor])
  
  print(class(vars))
  lvls <- ifelse(class(vars) == "numeric", list(seq(min(vars), max(vars), length.out = 3)), list(unique(vars)))
  print(lvls)
  print(class(lvls))
  lvlsr <- lapply(lvls, round, 2)
  print(lvlsr)
  lvlsrn <- as.numeric(unlist(lvlsr))
  print(class(lvlsrn))
  pdf(paste("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/reactivity/ReappraisalDirection*group4*", individualFactor, ".pdf"))
  lsm <- lsmeans(models, "ReappraisalDirection", by = c(individualFactor, "group4"), at =list(as.formula(paste(individualFactor = lvlsrn, "group4"= c("attempter", "depression", "control", "ideator")))))
  
  print(lsm)
  plt <- plot(lsm, horiz = F, xlab = "reappraisal type") +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    ggtitle(paste("Rating ~ ReappraisalDirection*group4*", individualFactor, "+ (1|ID)")) +
    facet_grid(as.formula(paste(". ~", paste(individualFactor, "+ group4"))))
  dev.off()
  print(plt)
  return(plt) 
})


```

```{r, group5}
# ---------------------------------------------------group5-------------------------------------------

# group5
## models loop through all vars by "rating = _type*group5 + i + (1|ID)"
VarLoop1 <- emoRating[, c("MMSE", "PROTECT2AGE", "GENDERTEXT", "IncomePerCapita", "HRSD_NO_SUI", "EDUCATION", "RACETEXT", "DRS", "EXIT", "BIS_NONPLAN", "urgency", "IIP15INTAMBV", "IIP15INTSEN", "IIP15AGRESS", "IRI_EMPATHETIC_CONCERN")]
varlist1 <- names(VarLoop1)
mReact5list1 <- lapply(varlist1, function(x) {
  lmer(substitute(scale(Rating) ~ ReappraisalDirection*group5 + i + (1|ID), list(i = as.name(x))), data = emoRatingScale)
})
mReact5list1_summ <- lapply(mReact5list1, summary)

## loop through all vars by "rating = ReappraisalDirection*group5*i + (1|ID)"
VarLoop2 <- emoRating[, c("MMSE", "EDUCATION", "IncomePerCapita", "GENDERTEXT", "PROTECT2AGE", "HRSD_NO_SUI", "BIS_NONPLAN", "urgency", "IIP15INTAMBV", "IIP15INTSEN", "IIP15AGRESS", "IRI_EMPATHETIC_CONCERN")]
varlist2 <- names(VarLoop2)

mReact5list2 <- lapply(varlist2, function(x) {
  lmer(substitute(scale(Rating) ~ ReappraisalDirection*group5*i + (1|ID), list(i = as.name(x))), data = emoRatingScale)
})
mReact5list2_summ <- lapply(mReact5list2, summary)


for (i in mReact5list2_summ) {
  print(i$call)
  stargazer(i$coefficients, type = "text", title = paste("Rating ~ ReappraisalDirection*group5*", i, "+(1|ID)"),
            out = paste("/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/", i$call, ".txt"))
}


# group5 graphs
pltFun <- function(x){
  lsm <- lsmeans(x, "ReappraisalDirection", by = c("group5"))
  plt <- plot(lsm, horiz = F, xlab = "reappraisal type") +
    theme(axis.text.x=element_text(angle=90, hjust=1)) +
    facet_grid(. ~ group5)
  return(plt)
}


pltFun1 <- function(x){
  mEff <- allEffects(x)
  plt1 <- plot(mEff, axes = list(y = list(lab = "reactivity"))) +
    facet_grid(. ~ group5)
  return(plt1)
}

## non interaction graphs
plt_NonInter1 <- lapply(mReact5list1, pltFun)
print(plt_NonInter1)
for (i in plt_NonInter1) {
  for (j in varlist) {
    #jpeg(paste('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/rating=ReappraisalDirection*group5+', j, '.jpg'))
    plt_NonInter <- i + ggtitle(paste("Rating=group5*ReappraisalDirection+", j))
    dev.off()
    print(plt_NonInter)
  }
}

plt2 <- lapply(mReact5list1, pltFun1)
print(plt2)

## interaction model graphs
plt_Inter1 <- lapply(mReact5list2, pltFun)
print(plt_Inter1)

for (i in plt_Inter1) {
  for (j in varlist) {
    plt_Inter <- i + ggtitle(paste("Rating=group5*ReappraisalDirection*", j))
    dev.off()
    print(plt_Inter)
  }
}

plt1 <- lapply(mReact5list2, pltFun1)
print(plt1)

print(plt_Inter1)
print(plt_NonInter1)
lapply(mReact5list1, summary)
lapply(mReact5list2, summary)
```


```{r, IIP15AGRESS}
# IIP15AGRESS is significant at Rating = ReappraisalDirection*group5+IIP15AGRESS

# group4 
mReact4Agress1 <- lmer(
  scale(Rating) ~ ReappraisalDirection*group4+scale(IIP15AGRESS) + (1|ID), data = emoRating)

stargazer(summary(mReact4Agress1)$coefficients, type = "text", title = "Rating ~ ReappraisalDirection*group5+IIP15AGRESS + (1|ID)", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/rating=ReappraisalDirection*group4_IIP15AGRESS.txt")

jpeg('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/rating=group4*ReappraisalDirection+IIP15AGRESS.jpg')
lsm <- lsmeans(mReact4Agress1, "ReappraisalDirection", by = c("group4"))
plot(lsm, horiz = F, xlab = "reappraisal type") +
  facet_grid(. ~ group4) +
  ggtitle("IIP15AGRESS(no interaction with group and ReappraisalDirection)")
dev.off()
mEff <- allEffects(mReact4Agress1)
plot(mEff, axes = list(y = list(lab = "reactivity")))


# group5
mReact5Agress1 <- lmer(
  scale(Rating) ~ ReappraisalDirection*group5+scale(IIP15AGRESS) + (1|ID), data = emoRating)

stargazer(summary(mReact5Agress1)$coefficients, type = "text", title = "Rating ~ ReappraisalDirection*group5+IIP15AGRESS + (1|ID)", out = "/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/rating=ReappraisalDirection*group5_IIP15AGRESS.txt")

jpeg('/Volumes/LAB/Suicide_UG/UG_data_analysis/outputs/rating=group5*Qtype+IIP15AGRESS.jpg')
lsm <- lsmeans(mReact5Agress1, "ReappraisalDirection", by = c("group5"))
plot(lsm, horiz = F, xlab = "reappraisal type") +
  theme(axis.text.x=element_text(angle=90, hjust=1)) +
  facet_grid(. ~ group5) +
  ggtitle("IIP15AGRESS(no interaction with group and ReappraisalDirection)")
dev.off()
mEff <- allEffects(mReact5Agress1)
plot(mEff, axes = list(y = list(lab = "reactivity")))

```